# About the Text of Quran {#text}

In this chapter, I will mainly show, first, how to fetch the text of Quran into R programming environment, then compute some of the important descriptive numbers of the text of Quran but I will not analyse those numbers in this chapter and leave it to the chapters about evidences such as Chapter \@ref(Evidences).

I downloaded the text of Quran from tanzil.net/download. Arabic speakers do not need punctuation and thus there are no punctuation in the original text. I am not able to speak in more technical details as I do not know Arabic. After searching the internet, I found this tutorial (textminingthequran.com/tutorial/quran.html) and I followed it. As instructed in it, we go to the tanzil.net/download and select "Simple Clean" option without any pause marks or other options. For this, deselect "Include pause marks" and "Include sajdah signs" options. These are all not part of the simple and pure text but added later to ease the reading. Then select "Text(with aya numbers)" option and click download button. This way you will get a pure text of Quran in your computer with verse ("aya" in Arabic) numbers. In this file, there are "sura" numbers (sura is in Arabic for chapter) followed by verse numbers followed by the actual text of the verses. You can open it in a text editor and better see its structure. Each fields is separated by a bar "|" symbol and there is also some copyright notes at the end of the text, which are all added by tanzil.net as part of their. Therefore, as you will set below, while reading the downloaded text file into the R programming environment, we remove them first. 

Everything is made up from smaller components. When it comes to the text of a book, the main components are letters, words, verses and chapters. Therefore, I first searched over these components if there is any 19 based coding design pattern over them. As you will see in the evidences chapters, there are indeed 19 based coding system over the text of Quran. I think I could not solve all the system yet but the evidences I provide are sufficient to witness a beautiful and strong 19 based coding system of the text of Quran, which will be contributed by this book as further proofs to support the belief that Quran is intact and unchanged from the beginning.

In the following of this chapter, you will see how to fetch the text of Quran into R programming environment and also performs some basic text processing and get the important descriptive numbers of Quran.

An important point to  remind is that the structure of the text of Quran is also unique and not the same as any other we might come across. All the verses are numbered but there are 112 unnumbered and repeated Basmala verse in front of all the 112 chapter out of the 114 chapters. Also the first verse of the first chapter is the numbered Basmala verse. Moreover, Chapter 9 does not have any Basmala in contrary to the rest of 113 chapters but interesting enough Chapter 27 has a Basmala verse within its chapter within the context. So, it looks there is this non-standard structure and deliberate organization. It leave question whether to refer the total descriptive numbers (e.g. verse, words and letters) with respect to only the numbered verses or together (numbered and unnumbered Basmala verses). In my analysis, I analysed both of them and witnessed that they are designed together and both types of descriptive numbers are valid because they designed together as you will see in the evidences. So, I will always refer both of the type of the text of Quran with respect to, first, the numbered verses only and, second, the numbered and unnumbered verses together.

Before going any further, one tiny point I want to mention about the text of Quran is the punctuation. Arabic speakers do not need them and thus they are not part of the original text but they are added as helpers later on for non-Arabic speaks such as Turkish speaking people like me. I would not normally even talk about this point but when I had a discussion with one of my non-Muslim friends, he made an argument based on those punctuation and claimed that the text of Quran has been change as other wholly books. I was quite surprised that even such a simple fact was being used as an argument and he got this mis-information from the internet as later searched about this. Anyway, in short, punctuation are not part of the text of the text of Quran and does not included in text processing analysis. If one have doubts about it, she should feel free to speak to an Arabic expert about it.



## Fetching Quran's Text into R {#Fetchingtext}

In order to be able to process and analyse the text of Quran, we need to fetch it into an R console. For that, I utilized this very useful tutorial at [@getQuran]. As mentioned in that tutorial, I downloaded the text file of Quran from http://tanzil.net/download/ with "Simple Clean" option without any pause marks or other options, and also with the "Text (with aya numbers)" option selected. I then saved downloaded text file in a folder with the name "data" under the current working directory.

We can run this to read Quran text file into R programming environment:

```{r eval=TRUE}
tenzil = read.csv("data/quran-simple-clean.txt", header=F, stringsAsFactor=F, encoding="UTF-8", sep="|")
```

Let's see the head and tail of this text file to see if there is anything added to describe the text.

```{r eval=TRUE}
head(tenzil)
tail(tenzil)
```

It looks, the head of the data is clean and it is a table with three columns (a data frame in R). Each row contains one verse in order. First column contains the chapter numbers (or, in Arabic term, 'sura' numbers). Second column has verse numbers (or, in Arabic term, 'aya' numbers). Third column has the verses in Arabic.

However, there is some license related information appended to the tail of the text by tanzil.net. Let's find where to clean it at the tail of the text file.

```{r eval=TRUE}
tenzil[6234:6238,]
```

As we see the last verse appears to be in the row index of 6236. The last chapter (sura) in Quran is the Chapter Nas (sura-al-nas). Since it is very short, almost all Muslims would have memorized it and sometimes recite it in their regular daily prayers. Although, I am no expert in Arabic, I can also recognize it easily from the Arabic writing even without the helper punctuations that we non-Arabic speakers need to be able to read the Arabic text of Quran with the correct pronunciation. Without Arabic knowledge, even I can confidently recognize the last verse of Quran from the verse in the index 6236. So, as instructed in the tutorial, I remove the rest of the last verse to clean the additional general text related information added by tanzil.net.
I keep this table as an the R object and named as *quran* to remember that this object keeps all the words and letters of Quran that we hold in our hand.

```{r eval=TRUE}
quran <- tenzil[1:6236,]
tail(quran)
```
As we see, the first column of the table keeps the chapter number, the second column keeps verse number and the third column keeps the text of each verse. Basically, each row of this table keeps the information about one verse in order. Let's first give their correct names in English to the columns and see the table again.

```{r eval=TRUE}
colnames(quran) = c("chapter", "verse", "text")
head(quran)
```

Let's also add the row names of the table into the table. Row names should keep the verse order from beginning to end, which we can also test it later on. Since Quran has an order and the order is important, we start given independent verse index numbers from first verse to the last as row names to be able to correctly access them later. I name the column of this independent verse indices as "VerseI" in the table. It is important to remember that this column is given by us independently and the verse indices per chapter that we refer when we quote any specific verse in Quran (such as this formal notation: 74:30).

```{r eval=TRUE}
quran <- cbind(as.numeric(rownames(quran)), quran)
colnames(quran)[1] = "VerseI"
quran$VerseI <- as.numeric(quran$VerseI)
quran$verse <- as.numeric(quran$verse)
quran$chapter <- as.numeric(quran$chapter)
head(quran)
```

## The categories of the main descriptive numbers {#numcatgypes}

It is helpful to define the categories of the main descriptive numbers of the text of Quran to clarify this point. Because I will keep mentioning the categories of the numbers while defining the rules of the coding system in Chapter \@ref(RuleCombine) and later present evidences with them.

There are four main descriptive numbers of Quran: the number of chapters, verses, words and letters. All the categories of the descriptive numbers of the text of Quran, except chapters, has numbered type and also the numbered and unnumbered type together versions because of the unique structure and organization of Quran that we observe in the book of Quran in our hands today. Basically, each of the three categories has two types Since the number of chapters has only numbered version, this category has a single number. Therefore, there are 7 main descriptive numbers of the text of Quran. In this chapter, I will compute them blindly via only the computer programming and provide its codes so that you can also reproduce and test those numbers from the text of Quran.

## Number of chapters and verses, and sanity checks on the text {#textcv}

Let's now first check if the indices of verses are in correct order. I will perform two tests here. First by the sum of all the index numbers, second by a simple plot and see if we observe what we expect for. We know that sum of the unique integer numbers from 1 to n is nx(n+1)/2  (by Gauss formula). Therefore, sum of the indices of the verses must be 6236x6237/2 = 19446966. In your computer, make sure its precision is capable of dealing with large numbers. Alternatively, you can also use a big number calculator such as this one [@BigNC].

Now let's write a code to sum the index values in the table and see if it matches to 19446966 as it must be.

```{r eval=TRUE}
cat("the sum of verse index column VerseI is ",sum(quran$VerseI))
if(sum(quran$VerseI) == 19446966) 
  print("The sum of the indices of verses are correct and passed this test.")
```

The first sum test passed for the indices of the verses. But, still in the middle or any other part of it the indices might be multiple of two numbers or more than the maximum 6236. Let's see the minimum, which must be 1, maximum, which must be 6236, median, which must be 3118.5 (median of even number) from the data and also most importantly the number of unique indices that must be 6236 too.

```{r eval=TRUE}
print(paste("Minimum, Maximum, Median of VerseI is ",
    min(quran$VerseI),",", max(quran$VerseI),",",median(quran$VerseI)))
print(paste("Number of unique values of VerseI is ",length(unique(quran$VerseI))))
```

As we see all are correct as expected. Let's plot it and see if it is monotonically increasing from 1 to 6236.
```{r eval=TRUE}
plot(quran$VerseI)
```
The plot is exactly as we expected that is increasing monotonically from chapter 1 to 114. Let's now check in a similar way, if the chapter numbers are in order and then observe the maximum number.

```{r eval=TRUE}
plot(quran$chapter)
print("Unique chapter numbers regarding the order of text: ")
print(unique(quran$chapter))
```

The plot is exactly is as we expected as increasing in general but have horizontal lines at some points because of the long chapters.

So, based on the mathematical and visual tests, we conclude that the text of Quran analysed in this book, which was downloaded from tanzil.net, has no apparent error in its text regarding verse and chapter indices and ready for further analysis.

These sanity checks are purely based on mathematical blind computations on the text of Quran. Therefore, they also blindly provide the number of chapters as 114 and the number of verses as 6236. Therefore, these sanity checks provides reproducible tests to count the number of chapters and verses of Quran and they confirm that its number of chapters is 114, which will be denoted by '**c**' for the rest of the book, and number of verses is 6236, which will be denoted by '**v**' for the rest of the book in the R programming environment. If we include the unnumbered Basmala verses as well, then we get, an optional, total number of verses that includes all the numbered verses and all the unnumbered verses (112 Basmalas) together, which is equal to 6236+112=6348 and we denote this number by '**V**' for future reference. We will demonstrate how those numbers are part of 19 based coding system in the Chapter \@ref(Evidences).

```{r eval=TRUE}
c <-  114
v <- nrow(quran) #6236
V <- v+112       #6348
```


## Numbered and Unnumbered Verses of Quran

Regarding its importance for the analysis, I will separately address the numbered verses and the numbered and unnumbered verse together as the types of the text of Quran. Quran has an out of ordinary structure than we used to see in other usual books and in that sense it also stands as unique. There are 114 chapters and they are all numbered from 1 to 114 and ordered deliberately as is in Quran. There are also verses and they are also numbered from 1 to the end of the verses of each chapter. For example, the first chapter, also the most famous one, al-Fatiha has chapter number 1 and it has 7 verses and each verses are numbered from 1 to 7. There is no such concept of paragraphs that we used read in our books but in a sense each sentence or a group of sentences together corresponds to each verse and numbered. This is very useful when we refer to a specific verse in Quran as we can easily quote two numbers to refer to it precisely. As an example, 19:38 refers to the chapter 19 and verse 38. Some verses are long and some verses are very short.

However, there is another interesting structural situation in the text of Quran. There is a special verse, Basmala (بسم الله الرحمن الرحيم), which is the first verse of the first chapter, namely 1:1 regarding its formal chapter and verse numbers. The translation of Basmala is "In the name of God, the merciful, the compassionate". In Quran, this special verse is written before all the chapters except Chapter 9 of Quran and it is recited before start reciting any Quran verse by Muslims. In a sense, it is like a key. This makes Quran as a book consisting of numbered and unnumbered verses. Therefore, in the text analysis of Quran, I will consider two categories that represent the two fundamental structure of it. First one represents the whole Quran, including numbered and unnumbered verses. Second, represents only the numbered verses, which means without those repeated unnumbered Basmalas in front of chapters. Since, this numbered and unnumbered verses are part of Quran, they might have a role in the 19 based coding system of Quran. I will discuss about this and show some evidences on it in Chapter \@ref(Evidences). Now, I will generate a second object that keeps only the numbered verses of Quran for further analysis on it. Let's see first verses of some of the chapters in the main object that keeps the whole Quran.

```{r eval=TRUE}
print(quran$text[quran$verse<=2 & quran$chapter==1])
quran$text[quran$verse<=2 & quran$chapter==2]
quran$text[quran$verse<=2 & quran$chapter==3]
```

As we see, tanzil.net has themselves included all the Basmalas inside the first verse of each chapter contrary to the written hard copy text of Quran that Muslims have since the beginning till now. tanzil.net probably might have done so for computational reasons to simplify the organization of the text. I analysed both of those two structure types of the text and computationally showed (in Chapter \@ref(Evidences)) that the numerical codings also supports the structure of the authentic printed copy as is. So, in the following, I will generate the second main table by separating those unnumbered Basmalas and get the table that keeps only the numbered verses of Quran. 

```{r eval=TRUE}
require(data.table, quietly = T)
quran <- data.table(quran)
nQuran <- quran
nQuran$text <- gsub("^بسم الله الرحمن الرحيم ","",quran$text)
nQuran$text[nQuran$verse<=2 & nQuran$chapter==1]
nQuran$text[nQuran$verse<=2 & nQuran$chapter==2]
nQuran$text[nQuran$verse<=2 & nQuran$chapter==3]
Basmala <-quran$text[1] #keep for future reference
```

As we see, in this second object, only first chapter has first verse as Basmala and numbered but other chapters do not have it as this table contains only the numbered verses. Also, I assigned the special verse Basmala into the R object "Basmala" for future reference in this book. So this R object, denoted with *nQuran*, represents only the numbered verses of Quran. Let's add one more column that keeps chapter and verse numbers together for easy referencing from the data table that I present below.

```{r eval=TRUE}
require(DT, quietly = T)
knitr::kable(head(nQuran), booktabs = TRUE,
  caption = 'Table head of the numbered verses of Quran.')
```

For future reference and analysis, I will also generate another table from this table, which holds the chapter indices and the number of verses per chapter as follows. I will assign this table into the R object *dfVC* for future reference in this book.

```{r eval=TRUE}
require(data.table, quietly = T)
versecomb <- c()
for(j in 1:114){
  i <- which(nQuran$chapter==j)
  versecomb <- c(versecomb, nQuran$verse[i[length(i)] ])
}

dfVC <- data.table(cbind(c(1:114), versecomb))
colnames(dfVC) <- c("Chapter_index","Verse_sum")
datatable(dfVC,
          caption = 'Table: The chapter indices and corresponding sum of verses of numbered verses.',
          options = list(pageLength = 5, 
                              autoWidth = TRUE),
          rownames= FALSE)
```


## Some text mining {#texttm}

Let's prepare a more comprehensive data table that keeps some further information about the numbers of text of Quran using text mining tools of R. I utilized the tutorial in [@tmQuran] and the R package [@tokenizersRef] to get each word and its frequencies, even the frequencies of the letters of it. I used the R programming language but I also used the 'tokenizers' text mining R package [@tokenizersRef] to get each word from the text of Quran.

I prefer to keep this book for all readers and thus will not go into details of explaining each lines of the code chunk below. In short, it computes the numbers of words and letters in both types of the text of Quran. I will keep using these R objects in the rest of the book as needed in the coming chapters.

```{r eval=TRUE}
require(tokenizers, quietly = T)
#All words in numbered verses
words <- unlist(tokenize_words(nQuran$text))
w <-  length(words) # should be 77797
cat("Number of words in numbered verses is ", w)

#number of letters in numbered verses
letters <-  sapply(words, nchar)
l <- sum(letters) #should be 330709
cat("Number of letters in numbered verses is ", l)

#All words in numbered and unnumbered verses
Words <- unlist(tokenize_words(quran$text))
W <- length(Words) #should be 78245
cat("Number of words in numbered and unnumbered verses is ", W)
Letters <-  sapply(Words, nchar)
L <- sum(Letters) #should be 332837
cat("Number of letters in numbered and unnumbered verses is ", L)
```

Now, we obtained the number of words and letters per verse in both types of the text of Quran. Let's add this information into the table of the numbered verses of Quran as follows.

```{r nQuran6-table, eval=TRUE, tidy=FALSE}
vwords<- c()
vletters <- c()
for(i in 1:nrow(nQuran)){
  tmpw <- unlist(tokenize_words(nQuran$text[i]))
  vwords <- c(vwords,length(tmpw))
  vletters <- c(vletters,sum(nchar(tmpw)))
}
nQuran<- cbind(nQuran[,1:3],vwords, vletters,nQuran[,4])
colnames(nQuran)[6] <- "text"

require(data.table)
require(DT)

tmpN <- nQuran
tmpN$CV <- paste(nQuran$chapter,nQuran$verse, sep = ":")


datatable(tmpN,
          caption = 'Table of numbered verses of Quran',
          options = list(pageLength = 5, 
                              autoWidth = TRUE),
          rownames= FALSE)
```

From this data we can also get the number of **unique** words and its number of letters of Quran a presented in the next chapter. But, before that lets also generate the similar table for the whole Quran text, including unnumbered Basmala verses as follows. As see, we represent the table with *unQuran* R object to be able to use in the rest of the book.


```{r unQuran-table, eval=TRUE, tidy=FALSE}
unQuran <- c()
for(i in 1:114){
  if(!(i %in% c(1,9))) {
    tmp <- data.frame(1,i,0,4,19,as.character(nQuran$text[1]))
    colnames(tmp) <- colnames(nQuran)
    unQuran <- rbind(unQuran,tmp,
                     nQuran[nQuran$chapter==i,])}else{
                                        unQuran <- rbind(unQuran,
                                        nQuran[nQuran$chapter==i,])
                                        }
}
unQuran$VerseI <- c(1:nrow(unQuran))

tmpUN <- unQuran
tmpUN$CV <- paste(unQuran$chapter,unQuran$verse, sep = ":")


datatable(tmpUN,
          caption = 'Table of all verses of Quran',
          options = list(pageLength = 5, 
                              autoWidth = TRUE),
          rownames= FALSE)
```


### The number of unique words in Quran {#textTMuw}

We had assigned all the word in the text of Quran to R objects *words* and *Words* in the previous sections. They contain each unique word in both types of the text of Quran. Then, it is very easy to compute the number of unique words and generate a table of it as follows.

```{r , eval=TRUE, tidy=FALSE}
tmp <- table(words)
tmp2 <- table(Words)
identical(names(tmp),names(tmp2)) # TRUE
require(data.table)
uwordsTable<- data.table(uwords = names(tmp), 
                         count = as.numeric(tmp),countW = as.numeric(tmp2),
                         uletters=sapply(names(tmp), nchar) )

u <- nrow(uwordsTable) # u represents the number of uniqiue words
print(paste("The number of UNIQUE words in Quran is ", u,"."))

uwordsTable <- uwordsTable[order(-count)]

```


```{r uwords-table99, fig.cap="Table", eval=TRUE, tidy=FALSE}
datatable(uwordsTable,
          caption = 'Table of unique words of Quran',
          options = list(pageLength = 5, 
                              autoWidth = TRUE),
          rownames= FALSE)
```

As seen, Table \@ref(fig:uwords-table99) is very useful as we can easily access the number of usage (frequency) of any unique word in Quran (including numbered and unnumbered verses) from the frequency column **countW**. For example, we can see from the head of the table that the number of times the word '**Allah**' (or in Arabic 'الله'
), which is the primary name of God in Quran, is used 2265 times in the whole Quran.
Similarly, the column named as **count** keeps the frequency of the unique words used in the numbered verses of Quran. The column **uwords** keeps the unique words in the whole Quran. The column **uletters** keeps the number of letters of each of the corresponding unique words. Then, as we see it is easy to compute the number of unique words in Quran from this table alone, which is equal to the table's number of rows. 

This table is especially important and useful as there are already many claims that some words appear in Quran that align with their corresponding numbers in nature (such as the number of days). However, this is something, in my opinion mostly appeal to people with Arabic language knowledge. Therefore, I did not test any of such claims available in the literature already but I provided a searchable table in the online version of this book so that interested people can easily search the word of their interest and even test the available claims. 

Back to the main point, as we just calculated, the number of unique words in Quran is $$`r u`$$ and I assigned it to the object '**u**' in R programming environment to refer to this number later this book. Since numbered verses and, unnumbered and unnumbered verses together is all the same except the unnumbered Basmala verses, all the unique words and their frequency counts must be the same except for the 4 words of the Basmala verse. I therefore placed the counts of those unique words in the second and third columns for both types of the text separately. As mentioned before, one numbered Basmala verse is available in Quran 1:1 (chapter 1, verse 1) and therefore the number of unique words are the same in both numbered verses and, unnumbered and unnumbered verses together. This means the number of unique words in Quran is always $`r u`$.

### The number of letters in unique words of Quran {#textTMul}

If we count the number of letters in each of the unique words and multiply by its frequency in Table \@ref(fig:uwords-table99), we can find the number of letters in unique words of Quran. We can easily calculate this by summing the last column named as *uletters* in the table as follows: 

```{r eval=TRUE}
U <- sum(uwordsTable$uletters)
print(paste("The number of letters in UNIQUE words
            of Quran is ",U,"."))
```

So, we reproducibly demonstrated that the number of letters in **unique** words of Quran is $$`r format(U, scientific=F)`$$. We also denote this number as '**U**' and will use this *R* object name whenever we refer to this number in our analysis for the rest of the book. 


### Table of unique words of the Basmala verse {#Basmalatab1}

There is the special unnumbered Basmala verse in the beginning of 113 chapters out of 114 chapters. The first chapter and the first verse is a numbered Basmala verse.  
Therefore, only the 4 words of the Basmala has different total number counts regarding the both categories in the table of unique words. Here, I will present those words of Basmala by filtering them from the table of unique words from Table \@ref(fig:uwords-table99). This will provide us the frequencies of the words of the Basmala verse in Quran. This will be later used to show one of the evidences of the text of Quran. 


```{r Basmalas-table, eval=TRUE, tidy=FALSE}
BasmalaTable <- uwordsTable[count != countW]
BasmalaTable$count <- as.numeric(BasmalaTable$count)
BasmalaTable$countW <- as.numeric(BasmalaTable$countW)
BasmalaTable$uletters <- as.numeric(BasmalaTable$uletters)
knitr::kable(BasmalaTable, booktabs = TRUE,
  caption = 'Table head of the unique words of Basmala verse in Quran.')
```



### Number of words and letters in Quran {#textTMuwW}

We calculated the number of words and letters in Quran before  but let's summarize them here as they are important for the evidences.

We have already computed the number of all the words and letters in Quran previously. The number of words in the numbered verses of Quran, which is denoted as lowercase **w** for future references in this book. Second, the number of words in Quran (means, all Quran, including numbered and unnumbered verses.), which is denoted as uppercase **W** for future references.

In summary, we computed numbers in three different categories about the words of Quran from lowest to highest, which are denoted as u ($`r format(u, scientific=F)`$), w ($`r format(w, scientific=F)`$) and W ($`r format(W, scientific=F)`$).

There are two main and one derived numbers of letters in Quran to compute. The derived number is the number of letters in all the unique words of Quran that was previously derived from the unique words of Quran. We had computed this number before as $`r format(U, scientific=F)`$ in Chapter \@ref(textTMul) and denote it as **U** for future reference in the book.


The number of letters in the **numbered verses** of Quran is denoted by **l**, and the number of letters in the whole Quran (including numbered and unnumbered verses) is denoted by **L**. The number of letters in the numbered verses of Quran is computed as $`r format(l, scientific=F)`$ and it will be denoted as the lowercase letter **l** for the rest of the book to refer it in text and in R programming environment. Also, the number of letters in whole Quran is computed as  $`r format(L, scientific=F)`$ and it will be denoted as the uppercase letter **L** for the rest of the book.

## All Numbers in Quran: Chapter, Verse, Word and Letter.

If you google it, you come across different numbers regarding the number of verses, words and letters of Quran. The only common one is the number of chapters that is 114. If you ask 100 randomly selected Muslims about the number of words and letters of Quran, almost none of them can answer it. If you ask them for the number of verses, then most of them again cannot answer it, a very small portion of them might give varying numbers for it. The direct reason for that is, there is no well known and commonly accepted numbers for the number words and letters of Quran. There are also multiple version of numbers circulating around for the number of verses. The main reason for this situation is, to the best of my knowledge, there is no reproducible and testable open source software available to review and test these numbers by anyone interested. If there was such a case, everyone who writes about these numbers would be able to refer and quote it without any hesitation. Previously, in Chapter \@ref(texttm), I provided a reproducible open source code that allows easily reproduce and generate all the 9 different descriptive numbers about the text of Quran. In fact, if Quran is unchanged and intact, then there can only be unique numbers for various attributes of its text and all Muslims must quote those same numbers if needed. By summarizing all the 9 numbers here within a table, this sub-section will serve as a universal reproducible reference and will clarify the confusion on all of these numbers once and for all, as the numbers generated here are reproducible via testable R codes that can be run by anyone who wishes to test them.


### Fact: The 7 main numbers of the text of Quran {#Fact1}

From lowest to highest, the **main** numbers related to the text of Quran are as follows:

1. **The number of chapters in Quran is $`r c`$** (denoted as **c**). See Chapter \@ref(textcv) for the proof.
2. **The number of verses in Quran is $`r v`$** (denoted as **v**). See Chapter \@ref(textcv) for the proof.
3. **The number of verses in Quran by including unnumbered Basmala verses is $`r format(v+112, scientific=F)`$** (denoted as **V**). We just add the 112 unnumbered Basmala verses upon the number of the numbered verses, **v**.
4. **The number of words in numbered verses of Quran is $`r format(w, scientific=F)`$** (denoted as **w**). See Chapter \@ref(textTMuwW) for the proof.
5. **The number of words in Quran (including unnumbered verses) is $`r format(W, scientific=F)`$** (denoted as **W**). See Chapter \@ref(textTMuwW) for the proof.
6. **The number of letters in numbered verses of Quran is $`r format(l, scientific=F)`$** (denoted as **l**). See Chapter \@ref(textTMuwW) for the proof.
7. **The number of letters in Quran (including unnumbered verses) is $`r format(L, scientific=F)`$** (denoted as **L**). See Chapter \@ref(textTMuwW) for the proof.

```{r numbers-table, eval=TRUE}
dfnums <- data.frame(c,v,V,w,W,l,L)
# Table:
knitr::kable(dfnums, booktabs = TRUE,
  caption = 'Table of all the main descriptive numbers of the text of Quran.')
```

### Fact: The unique descriptive numbers of the text of Quran {#FactUniques}

The **unique** descriptive numbers related to the text of Quran are as follows:

1. **The number of unique words in Quran is $`r u`$** (denoted as **u**). See Chapter \@ref(textTMuw) for the proof.
2. **The number of letters in unique words in Quran is $`r U`$** (denoted as **U**). See Chapter \@ref(textTMul) for the proof.


## Could these numbers be counted and designed by the people? {#Coulditbe}

In chapters Chapter \@ref(Evidences), I presented reproducible evidences for the 19 based coding system in the text of Quran using all the 9 descriptive numbers of the text of Quran. However, the next question might be whether those evidences can be designed by a human or a group of people 1387 years ago or was it beyond the ability of mankind at that time? I preferred to discuss on this matter here before presenting the evidences to better comprehend the level of difficulty of designing such coded numbers in the text.

To be able to design the codings of the evidence of Chapter \@ref(Evidences), Chapter \@ref(EvidencesRewriting) and Chapter \@ref(OtherEvidences), these are some of the necessities:

- Manually count the number of chapters (*c*): This is doable and it was already known from the beginning.

- Manually count the number of verses in Quran (*v*): Given that there is limitations on the paper and pen and the very large number of verses, this is a bit difficult for one person but it is still doable by a group of about 20 people, including unbiased double checks.

- Manually count the number of unique words in Quran (*u*): There are $`r format(u, scientific=F)`$ unique words and $`r format(w, scientific=F)`$ words used in Quran (without repeated Basmala verses). Thus, it is fair to say,  practically it is impossible to count the number of unique words manually in Quran. 

This is very difficult to achieve manually even with a group of 1000 people. Because, even if they work on chapters separately, they first need to find each unique words in each chapter and then they need to compare the words among the 114 chapters and merge them together into a single list without making a single mistake. If they could work directly on all the words of the text, then they have to consider all the words of Quran, whose number was previously denoted as **w** that is equal to $`r format(w, scientific=F)`$ (excluding the repeated unnumbered Basmala verses). Then the total number of words pair comparisons to be performed can be found from the upper and lower triangles of the square matrix of this number $`r format(w, scientific=F)`$ as $(`r format(w, scientific=F)`$ * $`r format(w-1, scientific=F)`)$ = $`r format(w*(w-1), scientific=F)`$. Roughly speaking, more than 6 billion word pairs comparisons must be made between the words of the text of Quran to be able to decide the number of unique words of Quran. This is apparently impractical and thus impossible to perform manually by people. Additionally, they could only use papers (mostly on skin and with pen and not in abundance of those).


Anyway, let's say in a very very long time, possibly many years, a very very large group of people might, in theory, manually perform this task but, still, they cannot be sure if they did it correct unless the manual process is repeated independently at least twice by another two independent groups of around 1000 people each. So, to get this number right needs quite a big dedication by a very large number of people. In total, it might need around 3000 people and maybe a year of dedication to this task. However, in a small sized town, could they find that much people who has time and ability and papers and pens and motivation to perform this difficult task. Even if there is, would that much people have the same motivation to perform it right. What would be the motivating purpose of what they are doing at that time? Even if some of the 3000 people are made motivated by the explanation of the benefit of a coding system in a text, would all of them be made fully motivated. If not, some of them might not have taken it fully seriously what they are doing. And there is considerable chance that one of the three independent groups comes up with a different number than $`r format(u, scientific=F)`$. In that case, they have to find another independent group of 1000 people to repeat the same process or may be another independent group of 1000 people too to make sure the one differently calculated number does not leave any doubt in their minds. As we see, this does not seem to be a practical task to achieve 1387 years ago. Another very important point to mention is that, right or wrong, there is no historical record at all that mentions such a task or anything similar was performed or even discussed by the people of that time or by the Prophet Muhammad. In fact, in total, there are millions of detailed, wrong or right, historical narratives, called *hadiths* narrated from the time of Prophet Muhammad but there is nothing mentioned in regard to the necessities I just discussed on getting this particular number of Quran. I keep saying 'wrong or right' when I mentioned the historical records, *hadiths*, because a very small portion (around 7000) of them are 'considered or accepted' by Muslim Scholars to be truthful and even more, they do not agree with each other in many of them. However, to emphasize my point, I assumed all the historical records of narrated hadiths, which are known to be more than a million, and state that no such situation or anything similar are mentioned in them. Therefore, considering impracticality of manually getting the number of unique words right as $`r format(u, scientific=F)`$ and there is no historical record at all among more than a million of hadiths nor any other historical records afterwards, I rationally conclude that this number was never counted by Prophet Muhammad nor his companions at that time and thus cannot be designed by the people of that time when Quran was written down first. For extremely skeptical people, I also want mention that there is no historical record at all in literature for the 'unique number of words' in Quran until the 21st century. This brings us to two logical explanations for the coding evidences you will witness: It is either designed by God as implicitly mentioned in Quran "74:30. Over it is Nineteen" or it is by a mere random chance, which is almost impossible as we also calculated their probabilities in those chapters. In my rational opinion, those evidences could only be designed by a supernatural power in that time and the only logical explanation is that, it is the design of God as stated in the book under consideration. For me, this design is no much different than the fine tune that we observe all over the universe and in particular on earth that we have its knowledge in great detail, but no scientific explanation at all **for the source** of the force that causes these design. Since the text of Quran has many other 19 based codings too, as you will see in the rest of this book, observing all those independent codings in an old book has nothing to do with chance but a supernatural power is my conclusion. Furthermore, these evidences not only prove the text of Quran was miraculously designed but also protected for the last 1387 years and intact as it was in the beginning, just as we might expect from a divine book that speaks to our time. No matter you believe in God or not, if you cannot find a substantial error in these reproducible evidences and in the analysis of the text, then rationally, you might have to accept anyway this 'reproducible miracle' in the text of Quran after you witness.


