# Other Evidences {#OtherEvidences}

In this chapter, I will present some of the other evidences I hypothesized and witnessed to be under the 19 based coding system of the text of Quran. I will also validate and provide reproducible tests for some of the known important 19 based evidences on Quran.


## Evidences on Basmala {#EvonBasmala}

The key verse Basmala is written at the beginning of all the 113 chapters but Chapter 9. No one really knows exactly, why there is no Basmala verse in the beginning of Chapter 9 out of all the 114 chapters. But the text structure of Quran has this odd and unique situation and after witnessing all the evidences so far we conclude that this is another sign of the design of the text of Quran. Because, otherwise almost all the evidences would collapse. Considering the many evidences I presented so far, we now know that it is required that there must be no Basmala at the beginning of Chapter 9 as otherwise all the presented 19 based system of the text of Quran would be invalid. This odd situation further assures that the 19 based coding system of the text of Quran was deliberately designed. 

Basmala has many 19 based codings already known about it in the literature. I will present here a few of them that I realized while working on this book and did not see anywhere else. So all the Basmala evidences of this book are first time presented to the literature in this book to the best of my knowledge.

Since the main point of this book is to present reproducible 19 based codings of the text of Quran, Let's access Basmala first. I had presented all the unique words of Quran in Table \@ref(fig:uwords-table99) in Chapter  \@ref(textTMuw). Let's see the head of this table again. Because the Chapter 1 and Verse 1 is Basmala verse already and we can get access to this special verse and its four words along with their word frequencies in Quran.

```{r uwords-table3, eval=TRUE, message=FALSE}
require(tm)
knitr::kable(head(uwordsTable), booktabs = TRUE,
  caption = 'Table head of the unique words of Quran.')
```

As we see in above table, the first four rows of the table contains the four words of Basmala. Three of them are different names of God ("Allah" (or God), "the Gracious", "the Compassionate") and the first word ("In the name of") refers to them as "In the name of God, the Gracious, the Compassionate". Basmala is a very special verse and unique regarding all the other verses. It is the first verse of Quran as if it is the opening or key. Before starting to recite any verse, Muslims first recite Basmala verse as the opening. Let's introduce the first evidence on Basmala verse.

For the reference, to the best of my knowledge, Evidence \@ref(Ev0Basmala), Evidence \@ref(Ev1Basmala), Evidence \@ref(Ev2Basmala) are first time presented to the literature in this book, and it has been hypothesized, tested and discovered by myself. In case if I find out that any of these evidences had been available in another article, then, in such a case, I surely add a citation and update the online version of this book.

### Basmala and frequency of its words {#BasmalaFreq}


Although Basmala is a very short verse with only 4 words, there are many evidences on just Basmala verse with 19 already known, such as the number of its letters is 19. In this chapter, I will first present the one about the frequency of its words in whole Quran, which I discovered while writing this book. Let's first slice a separate table on just Basmala from the above Table \@ref(tab:uwords-table3)

```{r , eval=TRUE, message=FALSE}
B <- BasmalaTable
summ <- c(sum(B$count), sum(B$countW), sum(B$uletters))

#BasmalaTable <- uwordsTable[count != countW]
knitr::kable(BasmalaTable, booktabs = TRUE,
  caption = 'Table of the unique words of Basmala verses in Quran.')

cat("The sum of each of the first three columns:")
cat(t(as.data.frame(summ)))
```

Before going further, let's just mention one of the test results from the table for one of the very well known evidence on Basmala verse. Basmala verse has 19 letters as we see in the sum of the third column that shows the sum of the letters of each words in Basmala. 

Getting back to the main point now, based on the number of words of Basmala and number of its letters, I will present reproducible evidences just on the special Basmala verse.

In Evidence \@ref(Ev1Basmala) and Evidence \@ref(Ev2Basmala), I will test the total number of words of Basmala. There are two numbers with respect to the sum of the number of all the 4 words of Basmala, which are 2235 and 2683. 2235 is for the sum of the number the of 4 words on the numbered verses of Quran and 2683 is for the numbered and unnumbered verses together (whole Quran). Regarding the general rule (as in the Test 19) as usual, we always combine numbers by concatenating. Since there are only two numbers in this case, the only combinations are 22352683 and 26832235. So, in total, there are four numbers to be tested (2235, 2683, 22352683, 26832235.) and we will use both the default and the optional digit sum test from the global **Test 19** (Chapter \@ref(Test19)) regarding the word of Basmala. The reason I take the sum of the numbers of the 4 words of Basmala is because I am testing evidences on Basmala that consists of the 4 words. Considering individual words from the 4 words of Basmala is not that meaningful because what makes Basmala is the combination of the 4 words together. Also the 4 words of Basmala do not only appear in the Basmala verse but also in the other verses independently from each other. This approach would show the integrity and harmony of Basmala within the full text of Quran.

In Evidence \@ref(Ev0Basmala), I will use the sum of each words of Basmala and concatenate them as I do as in the general rule. See the section for more detail.

### Evidence on Basmala words 1 {#Ev1Basmala}

$$2683$$
Since the special verse Basmala itself is under consideration, I decided to count the number of its words together in Quran. The sum number of all the words of Basmala is 2683 and the digit sum of this number is exactly equal to 19. This number represents the total number of all the 4 words in the whole Quran, including numbered and unnumbered verses. This means Basmala was also coded with 19 based coding system with respect to the usage of its words over the whole Quran. Or, in other words, "74:30. Over it is Nineteen". If any of the individual words of Basmala were deleted or added in any parts of Quran, then not only this evidence would not hold but also all the previous evidences I presented based on words and letters would collapse. So, this evidence is also part of all the evidences I presented so far and part of the 19 based coding system of the text of Quran. Regarding the proof, I already generated this number 2683 from Table \@ref(tab:uwords-table3) in the previous chapter, Chapter \@ref(BasmalaFreq). One can visit and reproduce this number if wished. In this evidence, we have one number and two tests.

```{r , eval=TRUE, message=FALSE}
global_tested_nums <- global_tested_nums + 2 
global_success_nums <- global_success_nums + 1 
```

Also as a **fact**, but not as evidence, when the 112 unnumbered Basmala numbers are concatenated with the sum of Basmala words number, we get 1122235 that is also divisible by 19. Again this is just an interesting number but not considered under the system as I follow general rules of the system.


### Evidence on Basmala words 2 {#Ev2Basmala}

$$22352683$$

The total number of the words of Basmala in the numbered verses of Quran is 2235 and in the unnumbered and numbered verses (whole Quran) is 2683 as counted in Chapter \@ref(BasmalaFreq). There are two concatenation combinations of these numbers as discussed in Chapter \@ref(BasmalaFreq), one of which is 22352683. This number, 22352683, that combines the total frequencies of the words of the Basmala in both types of the text of Quran, is divisible by 19. Here is the proof:
```{r , eval=TRUE, message=FALSE}
as.numeric(as.bigz(22352683) %% 19)
```

This provides further evidence that Basmala was coded with 19 based coding system with respect to the usage of its words over the text of whole Quran and also the text of numbered verses as well. The design of Basmala is so obvious when we consider the absence of Basmala at the beginning of Chapter 9 of Quran. If people themselves had written this text, they would normally place another unnumbered Basmala in front of Chapter 9 as well but it would cause collapsing all the evidences on Basmala and also the other evidences I presented based on words and letters so far. Regarding the proof, I already generated these two numbers from Table \@ref(tab:uwords-table3) in the previous chapter, Chapter \@ref(BasmalaFreq). One can visit and reproduce these numbers if wished.

We applied both tests on this number, which make 4 tests and 1 success.
```{r , eval=TRUE, message=FALSE}
global_tested_nums <- global_tested_nums + 4 
global_success_nums <- global_success_nums + 1 
```

### Evidence on individual Basmala words harmony in whole Quran {#Ev0Basmala}

$$3445215331461572265115$$

When we concatenate all the frequencies of each words of Basmala in numbered verses and also the numbered and unnumbered verses of Quran we get this 20 digit large number. You can manually perform it yourself from the Basmala table given above, where you need to concatenate the 4 numbers of the column *count* and the other 4 numbers of the *countW*. Regarding the general rules, we can concatenate them in two directions and we apply the default divisibility by 19 test and also the optional digit sum test. In total, we perform 4 tests in this evidence. The digit sum of this large number is exactly 76, which is 19x4. This is even more interesting as Basmala verse has 4 words and 19 letters. Or, in other words, "74:30. Over it is Nineteen"! 
We observed that all the words of the special verse Basmala not only in harmony together by being under 19 based coding system of the text of Quran but also with the words in entire Quran encoded to represent a single Basmala that has 19 letters and 4 words! Although I do not add the 19x4 observation into the formal evidences, I still state this amazing observation as an important **fact**. Here is the proof for the digit sum of this large number.

```{r , eval=TRUE}
tmp1 <- paste0(BasmalaTable$count, collapse = "")
tmp2 <- paste0(BasmalaTable$countW, collapse = "")
tmp <- paste0(tmp1,tmp2)
tmp
digitsum(tmp)
```

I will calculate the probability for all the Basmala evidences together in the end. In this current evidence, we had 4 tests and 2 successes as the digit sum test passes in both directions.

```{r , eval=TRUE, message=FALSE}
global_tested_nums <- global_tested_nums + 4 
global_success_nums <- global_success_nums + 2 
```


### Overall Probability on Basmala {#ProbBasmala}

I presented three separate evidences on Basmala and to the best of my knowledge, they are first time presented to the literature in this book and they are new. Therefore, I calculate their probabilities together here and also add those evidences' tests to the global counters for later usage. I will also present two more well known evidences on Basmala for the readers who did not have any pre-knowledge about them.

There are, in total, 10 tests and 4 successes in the three previous evidences on Basmala. Let's calculate the probability of this observation as follows:

```{r , eval=TRUE, message=FALSE}
tmp <-binom.test(4, 10, p = (1/19),
                 alternative = c("greater"))
tmp <- tmp$p.value
cat(paste("The probability of 4 success out of 10 (with p=1/19) is:", tmp))
```


### Known evidence on Basmala letters {#EvBasmalaLett}

Basmala itself alone is apparently aligned with the verse on the 19 that is "74:30. Over it is Nineteen". I presented the number of letters of each of the 4 words of Basmala in the third column (column name "u.lengths") of Table \@ref(tab:uwords-table3) in Chapter \@ref(BasmalaFreq). As can be counted manually from the table, the total number of letters of Basmala is 19 and thus Basmala alone is under the 19 based coding system of the text of Quran. This also means that the total number of letters of all the 2683 Basmalas is also divisible by 19.

This fact was known from the beginning of the revelation of  Quran and there is no need to reference it. However, it is worth mentioning that along with the number of chapters, 114, and the number of letters of Basmala might be left so apparent as clues of the 19 based coding system so that Muslims can imagine researching on this direction and reveal the 19 based coding system of the text of Quran.

### Known evidence on Basmala numbers {#EvBasmalaNum}

There are in total 114 Basmala verses in Quran and it is divisible by 19. This may be considered as self-evident fact by Muslims but it is not easy to test manually if you are not keep reading Quran in Arabic. Because, there are 113 Basmalas at the beginning of each chapter but there is no Basmala at the beginning of Chapter 9. So, where is the last Basmala to get the number 114? As an ordinary Muslim, I was not even aware of this situation until I was investigating on number 19. While reading on this topic, I 'heart' that there is one other Basmala within Chapter 9. But, Chapter 9 consists of 129 verses and it is not that easy to find that Basmala within it as a slow reader in Arabic. Further, we have to check that there is no other Basmala as well in other chapters of the whole Quran. So, this is not easily testable information by someone who is not a good Arabic reader. Therefore, in the following I provide the reproducible proof of this evidence that there are, in total, 114 Basmala verses in Quran, which is divisible by 19. In Chapter \@ref(text), I had assigned the special Basmala verse into R object '*Basmala*'. I will search this text in the R object *quran* that keeps the text of whole Quran as follows:


```{r , eval=TRUE, message=FALSE}
#See verse 1 and 8 in the head of quran table for Basmala.
quran[1:9,]
#Get the indices of Basmalas in each verse.
i<- grep(Basmala, quran$text)
# See the length of indices of Basmalas in tthe table.
length(i)
```

As we witnessed, there are really 114 Basmala verses in whole Quran. This was a well known fact but here, a reproducible computational test to prove this evidence is provided to the literature.


### Evidence on individual Basmala words {#EvBasmalaIndividuals}

As we have studied so far, there are 4 words in Basmala. I also looked at its words individually to see if they have meaningful relation to 19 system and I ended up with this evidence.

Before starting explaining the evidence, let me give this information first. Out of those 4 words, Allah and Al-Rahman can never be used for any creature. Those two can only be used for God. Although there are some disputes, the word Raheem in the Al-Raheem of the Basmala verse is considered permissible to be used for humans as well. I am no expert on this topic but aware of this dispute. Feel free to do your own research on this topic if you wish. The last word "Bism" is already not a name of God. 

Back to the main point, in this evidence I will present the identical 19 based pattern that we witness on the two special words of Basmala, Allah and Al-Rahman. In this pattern, for each word, I concatenate their total word counts of these words and their number of letters. The digit sum of each of these resulting numbers are exactly 19. The rationale behind this approach is that, the number of letters in a word keeps a unique additional information for the word of interest. Therefore, testing a word count along with its number or letters is also meaningful approach. Here are the numbers for each word.

The word Allah has been used in the Basmala verse in this form

الله

for exactly 2265 times and it has 4 words. Moreover this exact word is the most frequently used word among all the 14870 unique words in Quran. We first concatenate the word count and the number of letters of that word and get the number to be tested as follows:
22654.
As the general rule of this book, we apply two basic mathematical tests to see if the number of interest is under the 19 based coding system of the text of Quran. That is either the number itself or the digit sum of the number is divisible by 19.
For the word, Allah, we have digit sum test that proved success as this: 

2+2+6+5+4 = 19. 

As we see the digit sum is exactly 19. If this was a single observation, I might have not consider this observation as evidence but would consider as a fact. However, the second exclusive word of the Basmala verse, Al-Rahman ( الرحمن ), has also exact same property, which proves that thus is a pattern. Al-Rahman has been used 
157 times and it has 6 letter, which yields the number to be tested as 1576. Then we have digit sum of it again as exactly 19.

1576 = 1+5+6+7 = 19.

Since these two words are exclusive for God only, it appears to be meaningful to witness such common pattern. Considering this, we can consider two success out of two numbers of an exclusive category.

I will not add this evidence into the global counter that shows the global probability of the 19 based system presented in this book. However, for this particular evidence, for each word we applied two tests. Therefore, overall, we have 2 successes out of 4 tests, which results this probability:

Binomial test to calculate this specific probability.

```{r , eval=TRUE, message=FALSE}
tmp <-binom.test(2, 4, p = (1/19),
                 alternative = c("greater"))
tmp <- tmp$p.value
cat(paste("The probability of 2 success out of
            4 tests (with p=1/19) is:", tmp))
```


As an additional fact, the word Al-Raheem ( الرحيم ) was used 146 times and it has 6 words. There is this such fact on its number 146+6=152/19=8.

However, this is a single example and no sign of a pattern observed yet. Therefore, I did not consider it either in the formal evidence or fact category of this book.


## Evidence on some words {#EvSomeWords}

Let's recall the unique words table. We can use this table to count the frequency of some specific words of interest. There are already existing **claims** that some words coincidence with their known numbers in nature such as 365 for 'day', 12 for 'moon' and so on. I wanted to try myself but realized that it is not that appealing to me as someone who does not know Arabic in sufficient detail. However, I mainly left this dynamic table for Arabic speaking people so that they can make their own tests based on the existing claims. In the online version of this book, one can paste the word of interest into the search box and find the frequencies of the pasted word easily.

In the following subsections, I will present some important evidences and facts, which I observed from this words frequency table.

```{r uwordsSearch-table, eval=TRUE, tidy=FALSE}
datatable(uwordsTable,
          caption = 'Table of the unique words of Quran',
          options = list(pageLength = 5, 
                         autoWidth = TRUE),
          rownames= FALSE)
```

### Evidence on the word Zikr {#EvAl-zikr}

As I mentioned earlier, Muslims believe that Quran is intact and unchanged and cannot be changed too. They believe so because of the following verse (15:9):

> "We, indeed We, it is We who have sent down the Reminder, and indeed it is We who will preserve it.", Quran, 15:9

In Arabic, this is the original verse:

> " إنا نحن نزلنا الذكر وإنا له لحافظون	 ", Quran, 15:9

Notably, God uses the word "The Reminder" to refer to Quran, and promise to preserve it but not the book form of Quran. Here, "The Reminder" (Al-Zikr) means the memorized form of Quran that is verbally recited. There are hundreds of thousands Hafiz (memorizers of whole Quran) people around the world today who fully memorized Quran as an historical tradition and conveyed the message as intact until today as God promised.

Back to the main point, God promises to preserve "The Reminder", Al-zikr (in Arabic:  الذكر ), and it has been used exactly 19 times in overall Quran. In this book, the claim is that we can use 19 based coding system of the text of Quran to test and witness that Quran has been preserved. Therefore, it is remarkable that the specific word Al-zikr (the Reminder) was used 19 times over all Quran verses. Feel free to copy and paste the Arabic word in the search box of the table and see the word count of it yourself in Quran.


Moreover, the word Zikr (Reminder) alone, without the "Al" definite article (The), was used 38 times (19x2) over all Quran verses. Feel free to copy and paste the Arabic word of Zikr ( ذكر ) in the search box of the table and see the word count of it in Quran yourself.

As an additional **fact**, this special verse 15:9, which declares that Quran (the Reminder) will be protected, is the 1824th verse out of all the 6348 verses of Quran and 1824 is also multiple of 19. This fact seems as another sign that might refer to the relation between the protection of Quran and 19 based system in its text.

### Facts on other related words {#EvOtherWords}

I will keep this section short by providing some related words and their frequencies. I will let you infer the potential relation to the book.

The word "get down" ( أنزل ) used 95 times (19 x 5).

The word "our revelations" (  بآياتنا ) used 57 times (19 x 3).

The word "promise (Vaad)" ( وعد ) used 38 times (19 x 2).


We knew, God **promised** to preserve the Reminder, revelations, which was sent down. Feel free to copy and paste the Arabic words in the search box of the table and see the word count of them yourself in Quran.

## Evidences on Allah and Al-Rahman word positions and frequencies  {#EvAllahAlRahmanPositionsMain}

In the evidences within this main chapter, I will present evidences that prove the positions and counts of the word God, in Arabic **الله** (**Allah**), and the other name Al-Rahman,
(**الرحمن**)
are individually and together have 19 based design. 


These evidences prove that the distribution of the names of God (in Arabic, Allah and Al-Rahman) is not random and under precise 19 based design. These evidences suggest that the positions of the word Allah and/or Al-Rahman in the text of Quran stand as if a backbone within verses. These evidences prove that **Allah** and/or **Al-Rahman** words in Quran must be in their current locations in the text and also in their current frequencies in each verse. This observations further support the main hypothesis of this book that the text of Quran is intact and unchanged and it is under 19 based design.

I had started hypothesizing evidences with only Allah word but then I recalled the verse 17:110, which specifically mentions another name of God, Al-Rahman (The Most Compassionate/The All-Merciful), along with Allah word.

> "Say to them (O Prophet!): "Call upon Him as Allah or call upon Him as al-Rahman; call Him by whichever name you will, all His names are beautiful. ..."

Therefore, I thought that there might be a 19 based coding evidences of the word Al-Rahman along with Allah word regarding this verse.

Therefore, in the sub-chapters of this chapter, in Evidence \@ref(EvAllahAlRahmanPositionsMain), I will provide the evidences that prove the positions and counts of Allah and Al-Rahman words over all the verses of Quran are under 19 based design individually and also together.

Lets first get the position and frequency of Allah word in each verse with respect to general verse index, chapter index, verse indices at each chapter and the frequency in each verse. These are all natural numbers that exist in the text.

Since I always use both types of the text of Quran in this book , I will again get the related numbers for both of them. To recall, the main one text type is for all 6348 verses including unnumbered Basmala verses. And the second one is only for the 6236 numbered verses text type.

Here I obtain the numbers from the text and present the two tables with the obtained numbers for both text types. These are dynamic tables and you can access any data in it easily in the eBook.

```{r eval=TRUE}
require(data.table, quietly = T)
require(DT, quietly = T)
require(stringr)

#Allah word in Arabic is assigned to search within Quran
tmppattern <- "الله"

x <- unQuran #6348 verses
#find verse indices
tmp <- x$text 
tmp<- as.character(tmp)
j <- rep(0,length(tmp))
for(i in 1:length(tmp)){
  tmpw <-strsplit(tmp[i], " ")
  tmpw <- unlist(tmpw)
  j[i] <-sum(tmpw == tmppattern)
  rm(tmpw)
}
#if correct, this should result 
#2265 Allah words used in total within Quran.
sum(j)

#Get the verse indices where Allah word is used
i <- which( j!=0)
x <- x[,c(1:3)]
y <- cbind(x,j)
y <- y[i,]
colnames(y)<-c("Gen_verseI",
               "Chapter",
               "verse",
               "countW")
yunQ <- y
rm(y)
## do the same for 6236 numbered verses
x <- nQuran #6236 verses
#find verse indices
tmp <- x$text 
tmp<- as.character(tmp)
j <- rep(0,length(tmp))
for(i in 1:length(tmp)){
  tmpw <-strsplit(tmp[i], " ")
  tmpw <- unlist(tmpw)
  j[i] <-sum(tmpw == tmppattern)
  rm(tmpw)
}
#if correct, this should result 
#2153 Allah words used in total within Quran.
sum(j)

#Get the verse indices where Allah word is used
i <- which( j!=0)
x <- x[,c(1:3)]
y <- cbind(x,j)
y <- y[i,]
#
colnames(y)<-c("Gen_verseI",
               "Chapter",
               "verse",
               "countW")
ynQ <- y
rm(y)
##
datatable(yunQ,
          caption = 'Allah word positions and counts in 6348 verses',
          options = list(pageLength = 10, 
                              autoWidth = TRUE),
          rownames= FALSE)

datatable(ynQ,
          caption = 'Allah word positions and counts in 6236 verses',
          options = list(pageLength = 10, 
                              autoWidth = TRUE),
          rownames= FALSE)

#initialize the special counters to this chapter for probability calculations
AllahWordEvidenceTrials <- 0
AllahWordEvidenceSuccesses <- 0
```


Similarly, here we obtain the similar table for the word Al-Rahman only as follows:


```{r eval=TRUE}
#Al-Rahman word in Arabic is assigned to search within Quran
tmppattern <- "الرحمن"

x <- unQuran #in 6348 verses
#find verse indices
tmp <- x$text 
tmp<- as.character(tmp)
j <- rep(0,length(tmp))
for(i in 1:length(tmp)){
  tmpw <-strsplit(tmp[i], " ")
  tmpw <- unlist(tmpw)
  j[i] <-sum(tmpw == tmppattern)
  rm(tmpw)
}
#if correct, this should result 
# 157 Al-Rahman words used in total within Quran.
sum(j)

#Get the verse indices where Allah word is used
i <- which( j!=0)
x <- x[,c(1:3)]
y <- cbind(x,j)
y <- y[i,]
colnames(y)<-c("Gen_verseI",
               "Chapter",
               "verse",
               "countW")
yunQ2 <- y
rm(y)
## do the same for 6236 numbered verses
x <- nQuran #in 6236 verses
#find verse indices
tmp <- x$text 
tmp<- as.character(tmp)
j <- rep(0,length(tmp))
for(i in 1:length(tmp)){
  tmpw <-strsplit(tmp[i], " ")
  tmpw <- unlist(tmpw)
  j[i] <-sum(tmpw == tmppattern)
  rm(tmpw)
}
#if correct, this should result 
# 45 Al-Rahman words used in total within Quran.
sum(j)

#Get the verse indices where Allah word is used
i <- which( j!=0)
x <- x[,c(1:3)]
y <- cbind(x,j)
y <- y[i,]
#
colnames(y)<-c("Gen_verseI",
               "Chapter",
               "verse",
               "countW")
ynQ2 <- y
rm(y)
##
datatable(yunQ,
          caption = 'Al-Rahman word positions and counts in 6348 verses',
          options = list(pageLength = 10, 
                              autoWidth = TRUE),
          rownames= FALSE)

datatable(ynQ,
          caption = 'Al-Rahman word positions and counts in 6236 verses',
          options = list(pageLength = 10, 
                              autoWidth = TRUE),
          rownames= FALSE)
```

Now in the following, we obtain another similar table, that is obtained considering any verse that includes either Allah or Al-Rahman words or both in it.


```{r eval=TRUE}
#Allah and Al-Rahman word in Arabic is assigned to search within Quran
tmppattern <- "الله"
tmppattern2 <- "الرحمن"
x <- unQuran #in 6348 verses
#find verse indices
tmp <- x$text 
tmp<- as.character(tmp)
j <- rep(0,length(tmp))
for(i in 1:length(tmp)){
  tmpw <-strsplit(tmp[i], " ")
  tmpw <- unlist(tmpw)
  j[i] <- sum(tmpw == tmppattern) + sum(tmpw == tmppattern2)
  rm(tmpw)
}
#Allah and/or Al-Rahman words used in total within Quran.
sum(j)

#Get the verse indices where Al-Rahman word is used
i <- which( j!=0)
x <- x[,c(1:3)]
y <- cbind(x,j)
y <- y[i,]
colnames(y)<-c("Gen_verseI",
               "Chapter",
               "verse",
               "countW")
yunQ4 <- y
rm(y)
## do the same for 6236 numbered verses
x <- nQuran #in 6236 verses
#find verse indices
tmp <- x$text 
tmp<- as.character(tmp)
j <- rep(0,length(tmp))
for(i in 1:length(tmp)){
  tmpw <-strsplit(tmp[i], " ")
  tmpw <- unlist(tmpw)
  j[i] <-sum(tmpw == tmppattern) + sum(tmpw == tmppattern2)
  rm(tmpw)
}
#Allah and Al-Rahman words used in total within Quran.
sum(j)

#Get the verse indices where Allah word is used
i <- which( j!=0)
x <- x[,c(1:3)]
y <- cbind(x,j)
y <- y[i,]
#
colnames(y)<-c("Gen_verseI",
               "Chapter",
               "verse",
               "countW")
ynQ4 <- y
rm(y)
##
datatable(yunQ,
          caption = 'Allah and/or Al-Rahman word positions and counts in 6348 verses',
          options = list(pageLength = 10, 
                              autoWidth = TRUE),
          rownames= FALSE)

datatable(ynQ,
          caption = 'Allah and/or Al-Rahman word positions and counts in 6236 verses',
          options = list(pageLength = 10, 
                              autoWidth = TRUE),
          rownames= FALSE)
```

Now we can use these three tables in the following sections for coding evidences.


For the reference, to the best of my knowledge, All the evidences presented in the subsections of this Chapter \@ref(EvAllahAlRahmanPositionsMain) is first time presented to the literature in this book, and it has been hypothesized, tested and discovered by myself. In case if I find out that the evidences under Evidence \@ref(EvAllahAlRahmanPositionsMain) had been available in another article, then, in such a case, I surely add a citation and update the online version of this book. 



In summary, this is the main chapter that includes the three sub-chapters. I collected them in this main chapter because in each of the three sub-chapters, I use all the three tables for any coding tests. This means they have the common numbers to be tested. Each sub-chapter test for a different coding pattern. Therefore, this chapter will prove that, the positions and counts of Allah and Al-Rahman words over all the verses of Quran are under 19 based design individually and also together. To recall, the reason I consider the word Al-Rahman along with Allah word is because of the verse 17:110 in Quran.

> "Say to them (O Prophet!): "Call upon Him as Allah or call upon Him as al-Rahman; call Him by whichever name you will, all His names are beautiful. ..."



### Evidence on Allah and Al-Rahman words with concatenation of chapter and special verse indices {#EvAllahAlRahmanPosConcat}

In this evidence, we will witness that the exact positions of Allah and/or Al-Rahman is not random but coded into the text regarding chapter indices and special verse indices. In fact these are the most natural way of referring any verse in the text of Quran. For example when refer to a specific verse, we say 17:110, which means Chapter 17 and Verse 110. Therefore the evidences in this sub-chapter use the most natural numbers to refer to a position of a verse in the text of Quran. The coding pattern of the evidences of this sub-chapter concatenates each chapter index and special verse index with Allah and/or Al-Rahman words in it. In this evidence, I will prove that the chapter indices and the special verse indices with Allah words and/or Al-Rahman words in them are under 19 based design Since the same pattern exist in most of the trials, this is a very powerful evidence. We witness that the same 19 based design pattern exist considering only Allah word, only Al-Rahman word and also in their combination (verse with Allah or Al-Rahman words). Since as a global rule, I try any coding pattern in both of the text types of Quran (all 6348 verses or only 6236 numbered verses), in the end we perform 6 trials. As we will witness that 4 out of 6 trials are successful. This means the probability of such an observation is 1 in 10000 (or 0.0001) if we consider only these evidences independently.

```{r eval=TRUE}
tmp <-binom.test(4, 6,p = (1/19),
                 alternative = c("greater"))
tmp <- tmp$p.value

cat(paste("The probability of 4 success out of 
          6 tests (with p=1/19) is:", tmp))
```

Let's also add these numbers to the counters that we will use them in the probability calculations of the system in this book.

```{r eval=TRUE}
#counters to compute the overall probability
AllahWordEvidenceTrials <- AllahWordEvidenceTrials + 6
AllahWordEvidenceSuccesses <- AllahWordEvidenceSuccesses + 4
```


Now, Let's witness the evidences regarding each of the three numbers from tables we had obtained in the main chapter. 

**The Evidence (A) on Allah words:**

This evidence concatenates each chapter index and special verse index with only Allah words in it. The same pattern exist in both text categories (6348 and 6236 verses) of Quran.  First, I present the proof for the numbered 6236 verses below:

```{r eval=TRUE}
#The required numbers for this evidence are in the ynQ object. 
x<- ynQ #6236 numbered verses
tmp <- paste0(x$Chapter,x$verse)
# head and tail sides of numbers of each verse
head(tmp)
tail(tmp)
tmp <- paste0(tmp, collapse = "")
as.bigz(tmp) %% 19 #mod 19 must be zero

cat("number of digits on this big number is", nchar(tmp))
```

As we witnessed, the resulting 5732 digits length big number is multiple of 19.
You can access this `r nchar(tmp)` digits length big number from the following link:

https://github.com/quran2019/Quran19/blob/master/Evidence_7.3.1.A.txt

One can just copy the big number and paste it into a web based big number calculator and test it herself.

As a general rule of this book, I always try any coding pattern of any evidence in both of the text categories of Quran. Now as per the rule, I try the same coding pattern in all the 6348 verses of Quran. As I prove below, the same coding pattern also exist in that too! 

```{r eval=TRUE}
#The required numbers for this evidence are in the yunQ object.
x<- yunQ #all 6348 verses
tv <-c()
for(j in 1:nrow(x)) {
  if(x$verse[j] != 0){#for all the numbered verses
    tmp <- paste0(x$Chapter[j], x$verse[j])
  }else{#For unnumbered Basmala verses
    tmp <- paste0(x$Chapter[j])
  }
  tv <- c(tv,tmp)
}
# head and tail sides of numbers of each verse
head(tv)
tail(tv)
tmp <- paste0(tv, collapse = "") 

as.bigz(tmp) %% 19 #mod 19 must be zero

cat("number of digits on this big number is", nchar(tmp))
```

The resulting 5964 digits length big number is multiple of 19.
You can access this `r nchar(tmp)` digits length big number from the following link:

https://github.com/quran2019/Quran19/blob/master/Evidence_7.3.1.A2.txt


One can just copy the big number and paste it into a web based big number calculator and test it herself.

We witnessed two evidences of the same coding patterns, which proves that the exact positions of Allah words are perfectly under 19 based coding system of the text of Quran. Since, we observed this in two different text category, in total we tested 3244 verses that include Allah words in them considering their exact chapter and special verse indices. Since this special word, Allah, spread through Quran as if a skeleton, it also supports the accuracy and intactness of all the verses and chapters of Quran. Because, if any one of the 6348 or 6236 verses were removed,the considered verses would be shifted and these codings would not hold anymore. Only the last 5 verses would not be supported by these evidences as they are in the tail and does not contain Allah word in it.

As an interesting **fact**,  since these two evidences of the same coding pattern are related to each other, I generally test the relation between them too. As we see the digit length of these numbers 5732 and 5964 have a 19 based coding relation. When we concatenate them, the resulting numbers is 57325964 and it is also multiple of 19.


**The Evidence (B) on Al-Rahman words:**

Now we will witness that the same coding pattern also exist in all the 6348 verse of Quran considering only Al-Rahman words in it too:

```{r eval=TRUE}
#The required numbers for this evidence are in the yunQ2 object.
x<- yunQ2 #all 6348 verses
tv <-c()
for(j in 1:nrow(x)) {
  if(x$verse[j] != 0){#for all the numbered verses
    tmp <- paste0(x$Chapter[j], x$verse[j])
  }else{#For unnumbered Basmala verses
    tmp <- paste0(x$Chapter[j])
  }
  tv <- c(tv,tmp)
}
# head and tail sides of numbers of each verse
head(tv)
tail(tv)
tmp <- paste0(tv, collapse = "") 

as.bigz(tmp) %% 19 #mod 19 must be zero

cat("number of digits on this big number is", nchar(tmp))
```

As we witnessed, the resulting 406 digits length big number is multiple of 19. You can access this `r nchar(tmp)` digits length big number from the following link:


https://github.com/quran2019/Quran19/blob/master/Evidence_7.3.1.B.txt

One can just copy the big number and paste it into a web based big number calculator and test it herself.


**The Evidence (C) on Allah and/or Al-Rahman words together:**

Now we will witness that the same coding pattern also exist in the numbered verses of Quran considering Allah and/or Al-Rahman words together in them too:

```{r eval=TRUE}
#The required numbers for this evidence are in the ynQ4 object.
x<- ynQ4 #all 6348 verses
tmp <- paste0(x$Chapter,x$verse)
# head and tail sides of numbers of each verse
head(tmp)
tail(tmp)
tmp <- paste0(tmp, collapse = "")
as.bigz(tmp) %% 19 #mod 19 must be zero

cat("number of digits on this big number is", nchar(tmp))
```

As we witnessed, the resulting 5887 digits length big number is multiple of 19. You can access this `r nchar(tmp)` digits length big number from the following link:

https://github.com/quran2019/Quran19/blob/master/Evidence_7.3.1.C.txt

One can just copy the big number and paste it into a web based big number calculator and test it herself.

Now considering the four codings evidences, we witnessed that Allah and Al-Rahman words are under 19 based designs, which further proves the intactness of Quran together along with all the rest of the evidences.



### Evidence on Allah and Al-Rahman word positions regarding general verse indices {#EvAllahRakmanPositionsGenVerseIndex}

In this evidence, I will prove that the general verse indices of the verses which includes Allah words and also Allah and/or Al-Rahman words together are also under 19 based design. Basically, we will only look at the general verse indices alone. Remember that in the evidences of this main chapter, Chapter \@ref(EvAllahAlRahmanPositionsMain), we always use the numbers from the three tables, Allah only, Al-Rahman only, and also  Allah and/or Al-Rahman words together. In this sub-chapter, we will witness that the same coding pattern exist regarding Allah only and also Allah and/or Al-Rahman words together.

As we will witness that 2 out of 6 trials are successful. This means the probability of such an observation alone is 0.036 and still statistically significant if we consider only these evidences independently.

```{r eval=TRUE}
tmp <-binom.test(2, 6,p = (1/19),
                 alternative = c("greater"))
tmp <- tmp$p.value

cat(paste("The probability of 2 success out of 
          6 tests (with p=1/19) is:", tmp))
```

Let's also add these numbers to the counters that we will use them in the probability calculations of the system in this book.

```{r eval=TRUE}
#counters to compute the overall probability
AllahWordEvidenceTrials <- AllahWordEvidenceTrials + 6
AllahWordEvidenceSuccesses <- AllahWordEvidenceSuccesses + 2
```


Now, Let's witness the evidences regarding each of the three numbers from tables we had obtained in the main chapter. 


**Evidence (A) on Allah word only**:

This evidence tests whether the general verse indices, in which there is Allah words has 19 based design. As we will see there is design considering the numbered verses. When we concatenate each general verse indices in the 6236 numbered verses, the resulting big number is multiple of 19. This clearly shows the positions of verses with Allah words in the numbered verses are under the 19 based design.

```{r eval=TRUE}
# ynQ is for Allah word for numbered verses
y <- ynQ #from 6236 numbered verses
tmp<- y$Gen_verseI
# head side of numbers of each verse
head(tmp)
tmp <- paste0(tmp, collapse = "")
as.bigz(tmp) %% 19 
```

You can access this `r nchar(tmp)` digits length big number from the following link:

https://github.com/quran2019/Quran19/blob/master/Evidence_7.3.2.A.txt


One can just copy the big number and paste it into a web based big number calculator and test it herself.

One more **interesting fact** on this big number is that the length of this big number is **5719** and it is also multiple of 19 as 19x301.



**Evidence (B) on Allah and/or Al-Rahman words together**:

This evidence tests whether the general verse indices, in which there is Allah and/or Al-Rahman words together have 19 based design. As we will see there is design considering all the verses. When we concatenate each of the the resulting general verse indices in the 6348 numbered verses, the resulting big number is multiple of 19. This clearly shows the positions of verses with Allah and/or Al-Rahman words together are under the 19 based design. Here is the proof.

```{r eval=TRUE}
# yunQ4 is for Allah and/or Al-Rahman words together
y <- yunQ4 #from all the 6348 verses
tmp<- y$Gen_verseI
# head side of numbers of each verse
head(tmp)
tmp <- paste0(tmp, collapse = "")
as.bigz(tmp) %% 19 
```

You can access this `r nchar(tmp)` digits length big number from the following link:

https://github.com/quran2019/Quran19/blob/master/Evidence_7.3.2.B.txt

One can just copy the big number and paste it into a web based big number calculator and test it herself.



**Fact:**

In the above evidence (A) for Allah words only, we tested the general verse indices. 
I also tested the corresponding special verse indices of each chapter with the same pattern. Interesting enough, there is also 19 based relation as a fact that further supports that particular evidence.
When we concatenate each special verse index in the 6236 numbered verses, the digit sum of the resulting big number is 12730 and it is multiple of 19 as 19x670. This suggests that the positions of special verses with Allah word in them have also 19 based design.

```{r eval=TRUE}
y <- ynQ #numbered verses
tmp<- y$verse
# head side of numbers of each verse
head(tmp)
tmp <- paste0(tmp, collapse = "")
digitsum(tmp)
digitsum(tmp) %% 19 #mod 19 must be zero
```

You can access this `r nchar(tmp)` digits length big number from the following link:

https://github.com/quran2019/Quran19/blob/master/Fact_7.3.2.fact.txt


### Fact on Allah and Al-Rahman word positions when paired {#EvAllahRahmanwordpaired}

In this fact, I will demonstrate that the chapter and the special verse indices of the verses which includes Allah words and the verses which includes Al-Rahman words are together also under 19 based design. Basically, we will pair those indices. The pattern of this fact is similar to what I presented in Evidence \@ref(EvPerChapter1) and Evidence \@ref(EvPerVerse2).
In this sub-chapter, we will witness that the same coding pattern exist between the indices of Allah and also Al-Rahman words.


```{r eval=TRUE}
# yunQ is for Allah word from all verses
# yunQ2 is for Al-Rahman word from all verses
tmpdf1 <- yunQ
tmpdf2 <- yunQ2 
x<- tmpdf1
tv <-c()
for(j in 1:nrow(x)) {
  if(x$verse[j] != 0){#for all the numbered verses
    tmp <- paste0(x$Chapter[j], x$verse[j])
  }else{#For unnumbered Basmala verses
    tmp <- paste0(x$Chapter[j] )}
  tv <- c(tv,tmp) }
length(tv)
tmpa <- tv
#
x<- tmpdf2
tv <-c()
for(j in 1:nrow(x)) {
  if(x$verse[j] != 0){#for all the numbered verses
    tmp <- paste0(x$Chapter[j], x$verse[j])
  }else{#For unnumbered Basmala verses
    tmp <- paste0(x$Chapter[j] )}
  tv <- c(tv,tmp)}
length(tv)
#Pair both vectors
tmp <- paste0(tmpa,tv)
#concatenate all the numbers
tmp <- paste0(tmp, collapse = "")

as.bigz(tmp) %% 19 #test for 19
nchar(tmp)
```

You can access this `r nchar(tmp)` digits length big number from the following link:

https://github.com/quran2019/Quran19/blob/master/Fact_7.3.3.txt

One can just copy the big number and paste it into a web based big number calculator and test it herself.


### Probability of the Evidences on Allah and Al-Rahman word positions and frequencies {#ProbEvAllahPositions}

In this section I will compute the probability of witnessing all the new evidences on Allah and Al-Rahman word positions and frequencies.

As you know, I had two special counters to get the total number of tests and total number of successes. Using the two special counters and Binomial test, we can calculate the probability of witnessing all those evidences that proves the 19 based coding system exist on Allah and Al-Rahman  word positions and frequencies. This **supports** the overall conclusion of this book such that the text of Quran was designed from the beginning and it is intact and unchanged for the last 1387 years since it was first written in 632. Here is the probability of observing all those evidences by chance alone:

```{r , eval=TRUE, message=FALSE}
tmp <-binom.test(AllahWordEvidenceSuccesses, 
                 AllahWordEvidenceTrials,
                 p = (1/19),
                 alternative = c("greater"))
tmp <- tmp$p.value

cat(paste("The probability of all the ", AllahWordEvidenceSuccesses, "success out of all the", AllahWordEvidenceTrials, " tests (with p=1/19) is:", tmp))

cat(paste("The probability of all the ", AllahWordEvidenceSuccesses, "success out of all the", AllahWordEvidenceTrials,
  " tests (with p=1/19) and Probability of number 19
  being in Quran together is:", tmp*(1/114)))
```

As we see this is small probability and the evidences we witnessed cannot occur by chance and thus should be designed by the Author of Quran. This is my rational conclusion based on this probability.


Let's try something else for extremely skeptical people. If some people think that we should have used **two times more tests**, I will not even look at the possible successes in that case and keep the success number the same but double the number of performed tests and see what would then be the probability as follows:

```{r , eval=TRUE, message=FALSE}
tmp <-binom.test(AllahWordEvidenceSuccesses, 
                 AllahWordEvidenceTrials*2,
                 p = (1/19),
                 alternative = c("greater"))
tmp <- tmp$p.value

cat(paste("The probability of all the ", AllahWordEvidenceSuccesses, "success out of all the", AllahWordEvidenceTrials*2, 
            " tests (with p=1/19) is:", tmp))

cat(paste("The probability of all the ", AllahWordEvidenceSuccesses, "success out of all the", AllahWordEvidenceTrials*2, 
  " tests (with p=1/19) and Probability of
  number 19 being in Quran together is:", tmp*(1/114)))
```

As we observed that the probability of observing the evidences we all witnessed in this section is still statistically significant as it is less than 0.05.

Now, I add these trials and successes on Allah and Al-Rahman word positions to the global counters for overall system probability calculations in the end of the book.

```{r , eval=TRUE, message=FALSE}
global_tested_nums <- global_tested_nums + AllahWordEvidenceTrials
global_success_nums <- global_success_nums + AllahWordEvidenceSuccesses
```




## Evidence on Chapter At-Tawbah {#EvSuraTavba}

There was a speculation over the last two verses (verse 128 and verse 129) of the 9th chapter of Quran, also named as At-Tawbah, by Rashad Khalifa in 1974. He has manipulated the text of Quran to be able to match the numbers to his made up numbers. Scientifically, this is unacceptable. Because once the data is changed, the result is not a discovery of an existing system but and invention of one's own made up and thus fake system claim. He removed the last two verses of the the 9th chapter of Quran, which are verses 9:128 and 9:129.

Most of the evidences of the 19 based system I discovered and published online as e-book in 2019 in this book already proves the intactness and perfection of the text of Quran. However, I hypothesized that Almighty God might have designed additional particular evidences on Chapter 9 considering this speculation. And, without much surprise I witnessed the evidences that clearly proves the 19 based design for the verses of Chapter 9. 

The clear coding evidence is on the verse indices of Chapter 9. In Evidence \@ref(EvAllVerses), We witnessed that when we concatenate the special verse indices, the resulting big number is multiple of 19. The same coding pattern also exist in Chapter 9. When we concatenate its **special verse** indices from 1 to 129, the resulting big number is multiple of 19 as follows:

```{r eval=TRUE}
#Evidence on special verse indices of Chapter 9
x<- unQuran
x<- x[x$chapter==9,]
#head of the indices to be concatenated
head(x$verse)
tmp9v <- paste0(x$verse, collapse = "")
as.bigz(tmp9v) %% 19 # test if mod 19 is zero
```

Here is the "`r nchar(tmp9v)`" digits length big number of this evidence:

"`r tmp9v`"

As we witnessed the special verse indices has exact same coding pattern with Evidence \@ref(EvAllVerses). This is interesting but this information was already known as I recall it from an internet forum. However, as a single evidence it was not as convincing as it should be. Then, I hypothesized that we might observe the same pattern with the general verse indices of Chapter 9 as well. Because it then proves that the 19 based coding design of Chapter 9 is not only available in special verse indices but also in **general verse indices** that connects the positions of those verse over all verses of Quran. And I discovered this new evidence as follows:


```{r eval=TRUE}
#Evidence on general verse indices of Chapter 9
x<- unQuran
x<- x[x$chapter==9,]
#head of the indices to be concatenated
head(x$VerseI)
tmp9V <- paste0(x$VerseI, collapse = "")
as.bigz(tmp9V) %% 19 # test if mod 19 is zero
```

Here is the "`r nchar(tmp9V)`" digits length big number of this evidence:

"`r tmp9V`"

As we witnessed, all the 129 verses of Chapter 9 has 19 based coding design both in special and also in general verse indices.

I then further hypothesized that the similar pattern might exist also in the content of Chapter 9. Therefore, I tested similar coding pattern this time by concatenation **the number of words** per its verse and discovered the following similar evidence with words.

```{r eval=TRUE}
#Evidence on number of words of verses of Chapter 9
x<- unQuran
x<- x[x$chapter==9,]
#head of the number of words to be concatenated
head(x$vwords)
tmp9w <- paste0(x$vwords, collapse = "")
as.bigz(tmp9w) %% 19 # test if mod 19 is zero
```

Here is the "`r nchar(tmp9w)`" digits length big number of this evidence:

"`r tmp9w`"

As we witnessed the number of words of verses of Chapter 9 has also the similar 19 based coding pattern. The probability of observing these three evidence is significantly low. However, I searched all the 114 chapters of Quran and **only Chapter 9 has these three 19 based coding at the same time**. Moreover, the digit sum of all the big numbers of these three evidences together is also divisible by 19. This **connects all these three evidences** independently to each other. This further supports the 19 based design among these three coding evidences of similar pattern. **Digit sum is the only option** to test the relation among these three numbers. Because each of these three big numbers are already multiple of 19 and thus either concatenation or sum of them already must be multiple of 19. The only test we could perform is the digit sum of these three big numbers and we observe that it is also multiple of 19 as follows:


```{r eval=TRUE}
#Digit sum of the three big numbers of Chapter 9

tmp <- paste0(tmp9v,tmp9V,tmp9w)
cat("The length of the digits of the
    three big numbers: ", nchar(tmp))
tmp <- digitsum(tmp)
cat("Digit sum number is: ", tmp)

tmp %% 19 # test if mod 19 is zero
```

As we witnessed, the three evidences have also another independent 19 based coding among themselves based on their digit sum. These three evidences and the fourth additional one that connects them, clearly prove the 19 based design in the verses of Chapter 9. An it is the only chapter with this coding pattern that proves its verses are clearly under 19 based system. No wonder it is Chapter 9. Because, there has been speculation over its last two verses (128, 129) by the Rashad Khalifa's fake and made up 19 system claim. Considering this, I hypothesized that God might have placed a special 19 based design in the verses of Chapter 9. And, without much surprise, I discovered these evidences on Chapter 9, which proves that its under a clear 19 based design. Also, remember these evidences are themselves are also additional upon all the main evidences of this book that proves the text of Quran is intact and unchanged. 


As the last process to do, let's add the number of successful evidences and the number of numbers to be tested regarding this evidence in a global object so that in the end of the book we can calculate the global probability using the counters.

```{r , eval=TRUE, message=FALSE}
#Because we apply only the default test to two numbers in this evidence.
global_tested_nums <- global_tested_nums + 8 
global_success_nums <- global_success_nums + 5
```


In the following, I will provide some further 19 based relations of Chapter 9 and the last two verses of Chapter 9. I present them as facts but not as evidences.

**Fact**

The only remaining number we could test is the number of letters. We do not observe similar pattern on the number of letters of Chapter 9 but in this case we still observe that **the total number of letters of Chapter 9 is 11115** and it is also multiple of 19!

**Other Facts**

Since the speculations were over the two verses, verse 128 and 129 of Chapter 9, I also tried some potential evidences and observed many interesting facts. I will present them here just as **fact**. Because, to claim them to be evidence I need to test all of them over all the last two verses of each chapter and I have no motivation for that yet. Because the above 4 evidences already proves that Chapter 9 has 19 based design and intact. However, for curious readers, I leave my findings here as **facts**. Let's first see all their numbers:

Chapter index: 9, Verse index:128, Number of words: 14, Number of letters:60
This makes total representation number as: 91281460

Chapter index: 9, Verse index:129, Number of words: 15, Number of letters:54
This makes total representation number as: 91291554

**Fact 1**
The sum of these two numbers is multiple of 19 as follows:

```{r eval=TRUE}
#Digit sum of the three big numbers of Chapter 9
tmp <- 91281460+91291554 # 182573014 
tmp %% 19 # test if mod 19 is zero
```

**Fact 2**
The sum of each of these 8 numbers is multiple of 19 as follows:

9+128+14+60 + 9+129+15+54 = 418 and 418/19 = 22

The sum of these numbers without the number of letters:

9+128+14 + 9+129+15 = 304 and 304/19 = 16

This means the sum of the number of letters also multiple of 19 but it is not any multiple, it is 114 that means the number of chapters!
60 + 54 = 114

The relation between the the number of letters and number of chapters does not seem to be coincidence. Because, additionally 60 represents the chapters with **even** number of verses and 54 represents the chapters with **odd** number of verses.  (I recall reading 60 + 54 = 114 and the even/odd relation on an internet forum previously.)

**Fact 3** 
Concatenation of just with chapter and verse indices:
9:128 and 9:129 makes 91289129 / 19 = 4804691

**Fact 4** 
Concatenation of just with verse indices and number of words verse:

Verse 128 has 14 words and verse 129 has 15 words. 

Concatenation of them makes 1281412915 and 1281412915 / 19 = 67442785.

**Fact 5** 
We generally refer to these two verses as 9:128 and 129
Sum of them 9+128+129 = 266 and 266/19= 14

9+128+129 = 266


Let me remind again, these are just interesting **facts** and presented here for mainly curious readers who may delve into it to test if any coding evidence exist with respect to all the other consecutive verses in Quran.



For the reference, to the best of my knowledge, Evidence \@ref(EvSuraTavba) is first time presented to the literature in this book, and it has been hypothesized, tested and discovered by myself. In case if I find out Evidence \@ref(EvSuraTavba) had been available in another article, then, in such a case, I surely add a citation and update the online version of this book. 

## Evidences on Chapters with multiple of 19 content {#EvChapContmult19}

In this evidence, I tested whether there is any 19 based design in indices of chapters of which its content, the words or letters, is multiple of 19. 

You can test the numbers from these dynamic tables easily:

```{r , eval=TRUE, tidy=FALSE}
require(data.table, quietly = T)
require(DT, quietly = T)
datatable(dfVCWL,
          caption = 'Total numbers of each category in all 6348 verses per chapter',
          options = list(pageLength = 5, 
                          autoWidth = TRUE),
          rownames= FALSE)
#
datatable(dfVCwl, 
          caption = 'Total numbers of each category in the 6236 numbered verses per chapter',
          options = list(pageLength = 5, 
                         autoWidth = TRUE),
          rownames= FALSE)

#Get the indices of chapter with multiple of 19
tmp <- dfVCWL$cWords #in 6348 verses
i1 <- which( (as.numeric(tmp) %% 19) == 0)
#10  21  41  76  87  95  96 112
tmp <- dfVCwl$cwords #in 6236 verses
i2 <- which( (as.numeric(tmp) %% 19) == 0)
#17  27  30  43  54  58  80 110
tmp <- dfVCWL$cLetters
i3 <- which( (as.numeric(tmp) %% 19) == 0)
#9  90 107
```

The way we get the number to be tested as follows: Firstly, from chapters of all the 6348 verse, I obtain the chapters whose number of words are multiple of 19. These 8 chapters have words with multiple of 19 in total:

"`r i1`"

And, these 8 chapters have words with multiple of 19 in total from the 6236 numbered verses text type of Quran:

"`r i2`"

And, these 3 chapters have letters with multiple of 19 in total from the both text types of Quran. Since the Basmala verse has 19 letters, it does not make differences between numbered or all verses types of the text:

"`r i3`"

There are **two different** 19 based design in these indices.

**First 19 based design:** The total number of unique indices is **exactly** 19!.here is the proof:

```{r , eval=TRUE, message=FALSE}
i <- unique(c(i1,i2,i3))
i <- sort(i)
cat(i)
cat("The total number of unique indices is ", length(i) )
```

**Second 19 based design:** When we concatenate those 19 indices in their natural order, namely, from first chapter to the end in ascending order, We get a long number and it is also multiple of 19. Here is the proof that it is multiple of 19:

```{r , eval=TRUE, message=FALSE}
tmp <- paste0(i,collapse = "")
cat("The representative number to be tested:")
tmp
as.bigz(tmp) %% 19 #mod 19 must be zero

cat("The length of the number is ", nchar(tmp) )
```

As the last process to do, let's add the number of successful evidences and the number of total numbers to be tested regarding this evidence in the global object so that in the end of the book we can calculate the global probability using the counters. 

```{r , eval=TRUE, message=FALSE}
#Because we got the special pattern from the 19 indices.
global_tested_nums <- global_tested_nums + 1 
global_success_nums <- global_success_nums + 1
```

For the reference, to the best of my knowledge, Evidence \@ref(EvChapContmult19) is first time presented to the literature in this book, and it has been hypothesized, tested and discovered by myself. In case if I find out Evidence \@ref(EvChapContmult19) had been available in another article, then, in such a case, I surely add a citation and update the online version of this book. 


## Evidences on words content {#EvVerseContmult19}

In the previous evidence, Evidence \@ref(EvChapContmult19), I tested whether there is any 19 based design in indices of chapters of which its content, the words or letters, is multiple of 19. And, we witnessed that there is such design considering both text categories of Quran together. Namely, there is 19 based design considering the content of both the 6348 and 6236 verses categories.

After witnessing this evidence, I had also presented another 19 based design example as a fact following that evidence. The reason I had presented it as a fact rather than as evidence is because it was a single example and I had not observed a pattern considering that single fact. I investigated around that fact in more detail and on the date 5-29-2020, I discovered a design pattern. I present it here in this section.

This evidence, considers the content of the chapters or verses with respect the total number of words in them. I discovered that in both, chapter and verse level, there is similar design pattern. So, this evidence consist of two 19 based coding examples, one in chapter level and the other in the verse level. 

The first 19 based design is at the chapter level. This is the one I had presented it as a fact rather than as evidence in Evidence \@ref(EvChapContmult19) previously. You can check the previous dynamic table to see the numbers at chapter level if you wish.

```{r , eval=TRUE, tidy=FALSE}


#Get the indices of chapter with multiple of 19
tmp <- dfVCWL$cWords #in 6348 verses
i1 <- which( (as.numeric(tmp) %% 19) == 0)
i1
```

The way we get the indices to be tested as follows: Firstly, from chapters of all the 6348 verse, we obtain the chapter indices whose number of words are multiple of 19. These 8 chapters have total number of words with multiple of 19:

"`r i1`"


**Evidence A:** When we concatenate these indices, the indices of the chapters with the number of words that is multiple of 19 considering the all the 6348 verse category, we observe that this long number is multiple of 19. Here is the proof:
```{r , eval=TRUE, message=FALSE}
tmp <- paste0(i1,collapse = "")
cat("The representative number to be tested:")
tmp
as.bigz(tmp) %% 19 #mod 19 must be zero

cat("The length of the number is ", nchar(tmp) )
```
Now, we witnessed a 19 based meaningful code example. It is alone, would not be sufficient to consider as evidence and thus I had presented it as only fact previously. However, as we will see in the following, there is similar pattern at the verse level too as follows:


**Evidence B:** In this evidence, similar to the previous pattern but at verse level data of the text, we find the verses with total number of words as multiple 19. We get the general verses indices considering all the 6348 verses. We then concatenate these indices, the general verse indices of the chapters with the number of words that is multiple of 19 considering the all the 6348 verse category, we observe that this long number is multiple of 19. Here is the proof:

```{r , eval=TRUE, message=FALSE}
tmp <- unQuran$vwords #in 6348 verses
i <- which( (as.numeric(tmp) %% 19) == 0)

cat("The number of verses with
    worse content as multiple of 19 is ",
    length(i))

cat("The general verse indices of the verses 
    with the number of words that are
    multiple of 19 considering all the 6348 verses: ")
cat(i)
# Concatenate the indices in the natural order
tmp <- paste0(i,collapse = "")
cat("The representative number to be tested:")
tmp
as.bigz(tmp) %% 19 #mod 19 must be zero

cat("The length of the number is ", nchar(tmp) )
```

As we witnessed with the above two evidences, the content of chapters or verses with respect to the total number of words in them are not random and have 19 based codings in them. There is also this further fact which might suggest that the two evidences share the similar pattern. When we sum the length of both big numbers if the two evidences, the sum is 591+17 = 608 and it is also multiple of 19.



As the last process to do, let's add the number of successful evidences and the number of total numbers to be tested regarding this evidence in the global object so that in the end of the book we can calculate the global probability using the counters. 

```{r , eval=TRUE, message=FALSE}
global_tested_nums <- global_tested_nums + 4 
global_success_nums <- global_success_nums + 2
```



**Fact:** There is also this 19 based design, which I considered as a fact and thus will present it as a fact. In the above evidence. I considered the general verse indices while getting the indices of the verses with word content as multiple of 19. Instead of that, If we take the chapter indices and special verse indices, together as a single representation number, of the verses with multiple of 19 word content, then again the digit sum of the big number is multiple of 19. The coding exist both, in 6348 and 6236 verses as the resulting big numbers are the same. Here is the proof: 

```{r , eval=TRUE, message=FALSE}
tmp <- nQuran$vwords
i3 <- which( (as.numeric(tmp) %% 19) == 0)
i3 <- paste0(nQuran$chapter[i3], nQuran$verse[i3])
# Concatenate the indices in the natural order
tmp <- paste0(i3,collapse = "")
cat("Digit sum of this big number is ", digitsum(tmp) )
digitsum(tmp) %% 19 #mod 19 must be zero

cat("The length of the representative number to be tested is ", nchar(tmp) )
```

Another interesting fact is that, in the above fact, if we also consider number of letters of both text categories and get the single representation number just like we did in Evidence \@ref(EvChapContmult19) in the previous section, then the digit sum of resulting big number is also multiple of 19. Here is the proof:

```{r , eval=TRUE, message=FALSE}
tmp <- unQuran$vletters #indices for letters in 6348 verses
i2 <- which( (as.numeric(tmp) %% 19) == 0)
i2<-as.numeric(i2)
lng <- length(i2)
for(ix in 1:lng){
  if(unQuran$verse[i2[ix]]==0) {i2[ix] <- as.numeric(unQuran$chapter[i2[ix]])}else{
    i2[ix] <- as.numeric(paste0(unQuran$chapter[i2[ix]], unQuran$verse[i2[ix]]) )}
}
#
tmp <- nQuran$vletters ##indices for letters in 6236 verses
i4 <- which( (as.numeric(tmp) %% 19) == 0)
i4 <- paste0(nQuran$chapter[i4], nQuran$verse[i4])
#combine all indices
#i1 and i3 are the same as in the above fact
i <- unique(c(i3, i2,i4))
i <- sort(i)
tmp <- paste0(i,collapse = "")
digitsum(tmp) %% 19 

cat("The length of the representative number
    to be tested is ", nchar(tmp) )
```


For the reference, to the best of my knowledge, Evidence \@ref(EvVerseContmult19) is first time presented to the literature in this book, and it has been hypothesized, tested and discovered by myself. In case if I find out Evidence \@ref(EvVerseContmult19) had been available in another article, then, in such a case, I surely add a citation and update the online version of this book.


## Evidences on only Allah word positions and frequencies regarding Chapters, Verses and Words {#EvAllahPositionsonly}


In this chapter, I will present three different evidences in three different sub-sections of this section, using **chapter indices**, **verse indices** and the number of **Allah word counts** in each of those verses. The reason I present them in three sub-section is because they each have different coding pattern. Since I observed mainly digit sum based coding in those evidences, as an exception to the global rule, I will also use the optional digit sum test to the numbers even though they have order information. Therefore, I will not include, the number of successes and trials of these three sub-sections into the global counters. This means, the three evidences of that we will witness in the section will not affect the global probability of the general system that we will  measure in the end. Therefore,in the chapter, I will calculate the probability of what we observe with those three evidences of the three sub-sections of this chapter. In each of the following three subsections we perform 4 tests and observe one successes. This means 3 successes out of 12 trials with each success probability of 1/19. Therefore, the probability of such observation by chance alone can be calculated as follows:

```{r , eval=TRUE, message=FALSE}
tmp <-binom.test(3, 12,p = (1/19),
                 alternative = c("greater"))
tmp <- tmp$p.value

cat(paste("The probability of 3 success out of 
          12 tests (with p=1/19) is:", tmp))

cat(paste("The probability of 3 success out of 12 tests (with p=1/19) 
and Probability of number 19 being in Quran together is:", tmp*(1/114)))
```


The three evidences in the following three sub-chapters have a particularly importance. Because, in the fake 19 based claim of Rashad Khalifa, they use the same three columns but individually (**chapter indices**, **verse indices** and the number of **Allah word counts**). By removing one of the verses, they make sure (!) each of these three columns are multiple of 19 individually! They clearly manipulate the text on a specific verse to make sure the numbers match to their made up fake system claim. The three evidences I present in the following three sub-sections prove that there is already a 19 based coding design considering the same three columns of data, chapter indices, special verse indices and the total number of Allah words at that verse. Since there is already a 19 based coding on the same three columns, it is fair to say that, they could not find this already existing 19 based codings with those three columns and made up their owns by manipulating the text. Manipulating the text is scientifically unacceptable. Because, no matter what the manipulators find in the end, their system claim belongs to the manipulators but not to the original text itself. Because, once you open up the door for manipulation, then you have to exhaustively search for all the space of the possible texts that could be generated by the manipulations and prove that what you show is statistically significantly different than all the rest of the possible codings in that space! Considering the size of the text of Quran, it is impossible to perform this task. This proves the point that, scientifically speaking, it is non-sense to consider any claim that manipulates the text. Anyone who searches for coding patterns in the text of Quran, must use one of the already available text copies that has been accepted and already being used by Muslims. Any approach that manipulates even a single letter of the text by his own choice is just non-sense. 

For the reference, to the best of my knowledge, Evidence \@ref(EvAllahPositionsonly) is first time presented to the literature in this book, and it has been hypothesized, tested and discovered by myself. In case if I find out Evidence \@ref(EvAllahPositionsonly) had been available in another article, then, in such a case, I surely add a citation and update the online version of this book


Let's get back to the main topic and see the evidences in the following sub-sections.


### Evidences on Allah word positions and frequencies regarding Chapters, Verses and Words {#EvAllahPositionsipair}

In these evidence, I will prove that the **chapter index**, **verse index** and **Allah word counts** are under 19 based design in combination of both of the text types of Quran. It means, the design is over both text at the same time! Basically, I will concatenate all the numbers in natural order as I did in this book earlier for some other evidences. This means any single shift of any of those numbers might break the 19 based design. This proves that the positions of Allah word are under 19 based designed in combination of both text types of Quran.

This is the way we will obtain the number to be tested:
We will concatenate chapter index, verse index and word count in the natural order for each text type. We will obtain two vectors for both text types. We will then pair these two vectors by concatenating to each other. This evidence pattern is similar to what I presented in Evidence \@ref(EvPerChapter1) and Evidence \@ref(EvPerVerse2). Note that in Evidence \@ref(EvPerVerse2) the length of the two vectors that are paired were not equal. Thus, the smaller vector had repeated pairing from its beginning to pair to the longer vector. The similar pattern also exist in this evidence. We have two unequal length vectors but when paired they show and incredible 19 based evidence that the positions of Allah words are under 19 based design together in both text type of Quran. Here is the proof:  

```{r eval=TRUE}
#Concatenate for 6348 verses
# Some verse indices are 0 and they should be removed
#as there is no number to represent them even 0
x<- yunQ
tv <-c()
for(j in 1:nrow(x)) {
  if(x$verse[j] != 0){#for all the numbered verses
    tmp <- paste0(x$Chapter[j], x$verse[j],x$countW[j])
  }else{#For unnumbered Basmala verses
    tmp <- paste0(x$Chapter[j], x$countW[j] )
  }
  tv <- c(tv,tmp)
}
cat("Length of the vector from 6348
    verses is ", length(tv))

#concatenate for 6236 verse
y <- ynQ
tmp<- paste0(y$Chapter,
             y$verse,y$countW)
cat("Length of the vector from 6348
    verses is ", length(tmp))

#Pair both vectors
tmp <- paste0(tv,tmp)
#concatenate all the numbers
tmp <- paste0(tmp, collapse = "")
#Test if mod 19 is 0
as.bigz(tmp) %% 19 
cat("number of digits on this
    big number is", nchar(tmp))
```

You can access this `r nchar(tmp)` digits length big number from the following link:

https://github.com/quran2019/Quran19/blob/master/Evidence_7.7.1.txt

One can just copy the big number and paste it into a web based big number calculator and test it herself.

As an interesting fact, for the big number obtained with the exact same pattern of this evidence for the word **Al-Rahman**, which is one of the three names of God in the Basmala verse, we observe that digit sum of the big number is multiple of 19 too.



### Evidence on Allah word positions and frequencies regarding Chapters, Verses and Words with sum {#EvAllahPositionwithsum}

In this evidence, I will show that the chapter indices, verse indices and Allah word counts together have a 19 based design in the numbered verses of the text of Quran with respect to their total sum. In the table of Allah word positions in 6236 verses above, I provided the chapter indices, verse indices in that chapter and Allah word counts in each verse. We will use those numbers in this evidence too. This pattern of this evidence is similar to what I presented in Evidence \@ref(EvPerChapter1) and Evidence \@ref(EvPerVerse2).

The sum of each of these numbers are 33697, 100228 and 2153, respectively. The total number of all these three numbers is equal to **136078** and it is multiple of 19 (in particular 19x7162).

```{r eval=TRUE}
tmp <- sum(ynQ[,c(2,3,4)])
cat("The total number is ", tmp)
as.bigz(tmp) %% 19 # mod 19 is zero
```

This further shows the positions and frequencies of Allah words have 19 based coding relation together in the numbered verses of Quran. 


### Evidence on Allah word positions and frequencies regarding Chapters, Verses and Words with digit sum {#EvAllahPositionwithdigitsum}

In this evidence, I will show that the chapter indices, verse indices and Allah word counts together have a 19 based design in the numbered verses of the text of Quran with respect to the digit sum of all the numbers in those three columns of data. In the table of Allah word positions in 6236 verses above, I provided the chapter indices, verse indices in that chapter and Allah word counts in each verse. We will use those numbers in this evidence and test their digit sum. 

```{r eval=TRUE}
x <- ynQ
tmp <- paste0(x$Chapter, x$verse,x$countW)
tmp <- paste0(tmp, collapse = "")
cat("The length of number the big number is ", nchar(tmp) )
tmp <- digitsum(tmp)
cat("The digit sum of the big number is ", tmp)
tmp %% 19 # mod 19 is zero
```

You can access this 7298 digits length big number from the following link:

https://github.com/quran2019/Quran19/blob/master/Evidence_7.7.3.txt


As we witnessed, not only the sum of the numbers are multiple of 19 as we see in the previous evidence, but also their digit sum is under 19 based design.

As an interesting fact, for the big number obtained with the exact same pattern of this evidence for the word **Al-Rahim**, which is one of the three names of God in the Basmala verse, we observe that the big number is multiple of 19 and also its digit sum of it is multiple of 19 too.

As an additional note, you may have noticed that I removed the zero indices while concatenating as they correspond to unnumbered Basmala verses. In this book, I never used zero index for the unnumbered Basmala verses as there is **no number**, including zero and it also makes difference in the divisibility. However, if anyone argues on this point there is this example: When zero is used, there is also a design pattern in 6348 verses as follows. Basically, when we concatenate chapter index, verse index and word count for each verse with Allah word and then concatenate all in their natural order again, the resulting big number is also multiple of 19.
But I do **not** consider this example neither as evidence nor fact. I just give you as an example for the sake of argument. 

```{r eval=TRUE}
y <- yunQ
head(y) # head of the table
tmp<- paste0(y$Chapter,
             y$verse,y$countW)
# head side of numbers of each verse
head(tmp) 
tmp <- paste0(tmp, collapse = "")
as.bigz(tmp) %% 19
```



### Fact on Allah word positions and frequencies with concatenation {#EvAllahPositionwtConcat}

In this fact, I will prove that the general verse indices, the chapter indices, the verse indices and Allah word counts are also designed in the numbered verses of Quran with respect to their concatenations as follows. It looks, more of the evidences about Allah word counts are in the numbered verses category.

In this fact, we concatenate the general verse index, the chapter index and the number of Allah words in that verse. For example, the first Allah word in the numbered verse of Basmala verse in the first chapter (Al-Fatiha), which has also the first general verse index. Thus, we get this representative number for it after concatenating in the natural order: 111. Similarly, the following verse with Allah word is at the general verse index 14 and in the second chapter with one Allah word. Thus, we get this 1421 as the representative number for it by concatenating in the natural order. This is done for all the verses with Allah words in it. Then we concatenate all of these representative numbers with each other in the normal order of the table. Then we get 9742 digits length big number and it is multiple of 19. Here is the proof of this test:
```{r eval=TRUE}
#yunQ4  # ynQ
y <- ynQ #ynQ is from 6236 verses
head(y)
tmp<- paste0(y$Gen_verseI, y$Chapter,
             y$countW)
# head side of numbers of each verse
head(tmp)
tmp <- paste0(tmp, collapse = "")
as.bigz(tmp) %% 19 #mod 19 must be zero

```

You can access this `r nchar(tmp)` digits length big number from the following link:

https://github.com/quran2019/Quran19/blob/master/Fact_7.7.4.txt

One can just copy the big number and paste it into a web based big number calculator and test it herself.


### Fact: General verse indices, Chapter and Special verse indices {#EvAllahPositionGenChapSpecVerses2}

In this **fact**, I will show that the general verse indices, the chapter indices and the special verse indices in each chapter with Allah words in it have also 19 based relation in all the verses.

This fact concatenates each general verse index, chapter index and special verse index that have Allah words in it considering all the 6348 verses. We then concatenate each of these representation numbers in its natural order. The resulting 12126 digits length big number is multiple of 19.

```{r eval=TRUE}
x<- yunQ #all 6348 verses
tv <-c()
for(j in 1:nrow(x)) {
  if(x$verse[j] != 0){#for all the numbered verses
    tmp <- paste0(x$Gen_verseI[j], x$Chapter[j], x$verse[j])
  }else{#For unnumbered Basmala verses
    tmp <- paste0(x$Gen_verseI[j],x$Chapter[j])
  }
  tv <- c(tv,tmp)
}

# head side of numbers of each verse
head(tv)
tail(tv)
tmp <- paste0(tv, collapse = "") 
as.bigz(tmp) %% 19 # mod 19 must be zero 

cat("number of digits on this 
    big number is", nchar(tmp))
```

You can access this `r nchar(tmp)` digits length big number from the following link:

https://github.com/quran2019/Quran19/blob/master/Fact_7.7.5.txt

One can just copy the big number and paste it into a web based big number calculator and test it herself.





## Overall Probability of all the novel Evidences {#Probofnovels}

In this section I will compute the probability of witnessing all the new evidences we witnessed so far in this book. As you know, I had two global counters to get the total number of tests and total number of successes in the whole book. Using the two global counters and Binomial test, we can calculate the probability of witnessing all those new evidences that proves the 19 based coding system exist and thus the text of Quran was designed from the beginning and it is intact and unchanged for the last 1387 years since it was first written in 632. Here is the probability of observing all those evidences by chance alone:

```{r , eval=TRUE, message=FALSE}
tmp <-binom.test(global_success_nums, 
                 global_tested_nums,
                 p = (1/19),
                 alternative = c("greater"))
tmp <- tmp$p.value

cat(paste("The probability of all the ",
          global_success_nums, "success out of all the",
          global_tested_nums, " tests (with p=1/19) is:", tmp))

cat(paste("The probability of all the ",
          global_success_nums, "success out of all the",
          global_tested_nums, " tests (with p=1/19) and Probability
          of number 19 being in Quran together is:", tmp*(1/114)))
```

As we see this is extremely small probability and the evidences we witnessed cannot occur by chance and thus must be designed by the Author of Quran. This is my rational conclusion after witnessing all these reproducible evidences.


Let's try something else for extremely skeptical people. If some people think that we should have used two times more tests, I will not even look at the possible successes in that case and keep the success number same but double the number of performed tests and see what would then be the probability as follows:

```{r , eval=TRUE, message=FALSE}
tmp <-binom.test(global_success_nums, 
                 global_tested_nums*2,
                 p = (1/19),
                 alternative = c("greater"))
tmp <- tmp$p.value
cat(paste("The probability of all the ", global_success_nums,
          "success out of all the", global_tested_nums*2, 
          " tests (with p=1/19) is:", tmp))

cat(paste("The probability of all the ", global_success_nums,
          "success out of all the", global_tested_nums*2,
          " tests (with p=1/19) and Probability of number 19 
          being in Quran together is:", tmp*(1/114)))
```

As we observed that the probability of observing the new evidences we all witnessed in this book is still extremely small and cannot occur by mere chance and thus it must be designed as is. This shows that the text of Quran is coded by the 19 based coding system, which also proves that the text of Quran was designed as is when it was first written in 632 and it is intact and unchanged for the last 1387 years. Furthermore, as an interesting fact, it is revealed to all humankind in 2019, which means 1387 years later, which is also 19x73 and also its digit sum is 1+3+8+7 is exactly 19. This fact (not claimed as evidence) is very interesting as it also incorporates the two common operations I used in this book. 


How about if we increase the tested numbers by four fold to make sure even the extremely skeptical person is satisfied on the point of the statistical significance of the presented evidences.

```{r , eval=TRUE, message=FALSE}
tmp <-binom.test(global_success_nums, 
                 global_tested_nums*4,
                 p = (1/19),
                 alternative = c("greater"))
tmp <- tmp$p.value
cat(paste("The probability of all the ", global_success_nums,
          "success out of all the", global_tested_nums*4,
          " tests (with p=1/19) is:", tmp))

cat(paste("The probability of all the ", global_success_nums,
          "success out of all the", global_tested_nums*4,
          " tests (with p=1/19)  and Probability of number 19
          being in Quran together is:", tmp*(1/114)))
```

As we see, we have statistically extremely significant probability and there is no doubt about about the design of the 19 based system of the text of Quran.

Before closing this chapter, I again increase the tested numbers by 6 fold to make sure no one has any doubt about the 19 based system of the text of Quran we witnessed is statistically significant and not expected to be observed by chance. This also helps compensating any possible mistake that I personally might have done unintentionally while calculating the probability of the presented system in general.

```{r , eval=TRUE, message=FALSE}
tmp <-binom.test(global_success_nums, 
                 global_tested_nums*6,
                 p = (1/19),
                 alternative = c("greater"))
tmp <- tmp$p.value
cat(paste("The probability of all the ", global_success_nums,
          "success out of all the", global_tested_nums*6,
          " tests (with p=1/19) is:", tmp))

cat(paste("The probability of all the ", global_success_nums,
          "success out of all the", global_tested_nums*6,
          " tests (with p=1/19)  and Probability of number 19
          being in Quran together is:", tmp*(1/114)))
```

As we see, we have statistically very significant probability and there is no doubt about about the design of the 19 based system of the text of Quran.